### 2021-03-10 paper/main.tex
chfjfyjfy

\documentclass[conference]{IEEEtran}
\IEEEoverridecommandlockouts
% The preceding line is only needed to identify funding in the first footnote. If that is unneeded, please comment it out.
\usepackage{cite}
\usepackage{amsmath,amssymb,amsfonts}
\usepackage{algorithmic}
\usepackage{graphicx}
\usepackage{textcomp}
\usepackage{xcolor}
\def\BibTeX{{\rm B\kern-.05em{\sc i\kern-.025em b}\kern-.08em
    T\kern-.1667em\lower.7ex\hbox{E}\kern-.125emX}}
\begin{document}

\title{Conference Paper Title*\\
{\footnotesize \textsuperscript{*}Note: Sub-titles are not captured in Xplore and
should not be used}
\thanks{Identify applicable funding agency here. If none, delete this.}
}

\author{\IEEEauthorblockN{1\textsuperscript{st} Given Name Surname}
\IEEEauthorblockA{\textit{dept. name of organization (of Aff.)} \\
\textit{name of organization (of Aff.)}\\
City, Country \\
email address or ORCID}
\and
\IEEEauthorblockN{2\textsuperscript{nd} Given Name Surname}
\IEEEauthorblockA{\textit{dept. name of organization (of Aff.)} \\
\textit{name of organization (of Aff.)}\\
City, Country \\
email address or ORCID}
\and
\IEEEauthorblockN{3\textsuperscript{rd} Given Name Surname}
\IEEEauthorblockA{\textit{dept. name of organization (of Aff.)} \\
\textit{name of organization (of Aff.)}\\
City, Country \\
email address or ORCID}
\and
\IEEEauthorblockN{4\textsuperscript{th} Given Name Surname}
\IEEEauthorblockA{\textit{dept. name of organization (of Aff.)} \\
\textit{name of organization (of Aff.)}\\
City, Country \\
email address or ORCID}
\and
\IEEEauthorblockN{5\textsuperscript{th} Given Name Surname}
\IEEEauthorblockA{\textit{dept. name of organization (of Aff.)} \\
\textit{name of organization (of Aff.)}\\
City, Country \\
email address or ORCID}
\and
\IEEEauthorblockN{6\textsuperscript{th} Given Name Surname}
\IEEEauthorblockA{\textit{dept. name of organization (of Aff.)} \\
\textit{name of organization (of Aff.)}\\
City, Country \\
email address or ORCID}
}

\maketitle

\begin{abstract}
This document is a model and instructions for \LaTeX.
This and the IEEEtran.cls file define the components of your paper [title, text, heads, etc.]. *CRITICAL: Do Not Use Symbols, Special Characters, Footnotes, 
or Math in Paper Title or Abstract.
\end{abstract}

\begin{IEEEkeywords}
component, formatting, style, styling, insert
\end{IEEEkeywords}

\section{Introduction}
Nowadays, keeping track of the domestic energy usage is a common scenario in order to know how much is the real-time watt consumption. 
Anyway, in the most cases there is a sensor connected to the main safety switch giving the total energy consumption. Instead, our scenario is more accurate since we have a energy sensor for each plug connected to 220V line. In the following paragraphs, we are presenting our \textit{proof of concept} (POC) which consists of three main parts: the smart plugs, the main server and the web interface. In our POC, we have modified the architecture described in \cite{8110428} obtaining a specific low-energy consume-driven infrastructure. This latter consists of three main parts: the smart plugs, a central processing unit and the web interface. These devices are connected to the a wireless router, so is home scenario described below. It's a simple idea: let's suppose for example to plug both the dishwasher and the washing machine to two different smart plugs, and the user set up the max power consumption available for his house. On the first use of home appliances, a default value is choose in order to avoid blackout, and then we register the maximum power usage for each appliance. The user could turn on only the devices with a power consumption lower than the available watts. This is simple idea opens to possible different security issues, implementations and improvements that will be discussed in the challenges section.

\section{General architecture}
As we already said, the architecture implemented is different from the usually provided by this type of system, also because the modern infrastructure relies on cloud computing or external services. Our implementation do not share information about the user, and keeps all the data in the main server, eventually providing the possibility to accessed from outside. Anyway, in this case is not true that a cloud-computing is better, even if is more scalable, if there is no power available at home, the plugs will not be managed correctly either in a decentralized infrastructure. Even worse in a cloud based system, the plugs could not work properly, if there is no internet connection. 
\par After describing some architectural design aspects,%
%\subsection{Maintaining the Integrity of the Specifications}
%
%The IEEEtran class file is used to format your paper and style the text. All margins, 
%column widths, line spaces, and text fonts are prescribed; please do not 
%alter them. You may note peculiarities. For example, the head margin
%measures proportionately more than is customary. This measurement 
%and others are deliberate, using specifications that anticipate your paper 
%as one part of the entire proceedings, and not as an independent document. 
%Please do not revise any of the current designations.
%
%\section{Prepare Your Paper Before Styling}
%Before you begin to format your paper, first write and save the content as a 
%separate text file. Complete all content and organizational editing before 
%formatting. Please note sections \ref{AA}--\ref{SCM} below for more information on 
%proofreading, spelling and grammar.
%
%Keep your text and graphic files separate until after the text has been 
%formatted and styled. Do not number text heads---{\LaTeX} will do that 
%for you.
%
%\subsection{Abbreviations and Acronyms}\label{AA}
%Define abbreviations and acronyms the first time they are used in the text, 
%even after they have been defined in the abstract. Abbreviations such as 
%IEEE, SI, MKS, CGS, ac, dc, and rms do not have to be defined. Do not use 
%abbreviations in the title or heads unless they are unavoidable.
%
%\subsection{Units}
%\begin{itemize}
%\item Use either SI (MKS) or CGS as primary units. (SI units are encouraged.) English units may be used as secondary units (in parentheses). An exception would be the use of English units as identifiers in trade, such as ``3.5-inch disk drive''.
%\item Avoid combining SI and CGS units, such as current in amperes and magnetic field in oersteds. This often leads to confusion because equations do not balance dimensionally. If you must use mixed units, clearly state the units for each quantity that you use in an equation.
%\item Do not mix complete spellings and abbreviations of units: ``Wb/m\textsuperscript{2}'' or ``webers per square meter'', not ``webers/m\textsuperscript{2}''. Spell out units when they appear in text: ``. . . a few henries'', not ``. . . a few H''.
%\item Use a zero before decimal points: ``0.25'', not ``.25''. Use ``cm\textsuperscript{3}'', not ``cc''.)
%\end{itemize}
%
%\subsection{Equations}
%Number equations consecutively. To make your 
%equations more compact, you may use the solidus (~/~), the exp function, or 
%appropriate exponents. Italicize Roman symbols for quantities and variables, 
%but not Greek symbols. Use a long dash rather than a hyphen for a minus 
%sign. Punctuate equations with commas or periods when they are part of a 
%sentence, as in:
%\begin{equation}
%a+b=\gamma\label{eq}
%\end{equation}
%
%Be sure that the 
%symbols in your equation have been defined before or immediately following 
%the equation. Use ``\eqref{eq}'', not ``Eq.~\eqref{eq}'' or ``equation \eqref{eq}'', except at 
%the beginning of a sentence: ``Equation \eqref{eq} is . . .''
%
%\subsection{\LaTeX-Specific Advice}
%
%Please use ``soft'' (e.g., \verb|\eqref{Eq}|) cross references instead
%of ``hard'' references (e.g., \verb|(1)|). That will make it possible
%to combine sections, add equations, or change the order of figures or
%citations without having to go through the file line by line.
%
%Please don't use the \verb|{eqnarray}| equation environment. Use
%\verb|{align}| or \verb|{IEEEeqnarray}| instead. The \verb|{eqnarray}|
%environment leaves unsightly spaces around relation symbols.
%
%Please note that the \verb|{subequations}| environment in {\LaTeX}
%will increment the main equation counter even when there are no
%equation numbers displayed. If you forget that, you might write an
%article in which the equation numbers skip from (17) to (20), causing
%the copy editors to wonder if you've discovered a new method of
%counting.
%
%{\BibTeX} does not work by magic. It doesn't get the bibliographic
%data from thin air but from .bib files. If you use {\BibTeX} to produce a
%bibliography you must send the .bib files. 
%
%{\LaTeX} can't read your mind. If you assign the same label to a
%subsubsection and a table, you might find that Table I has been cross
%referenced as Table IV-B3. 
%
%{\LaTeX} does not have precognitive abilities. If you put a
%\verb|\label| command before the command that updates the counter it's
%supposed to be using, the label will pick up the last counter to be
%cross referenced instead. In particular, a \verb|\label| command
%should not go before the caption of a figure or a table.
%
%Do not use \verb|\nonumber| inside the \verb|{array}| environment. It
%will not stop equation numbers inside \verb|{array}| (there won't be
%any anyway) and it might stop a wanted equation number in the
%surrounding equation.
%
%\subsection{Some Common Mistakes}\label{SCM}
%\begin{itemize}
%\item The word ``data'' is plural, not singular.
%\item The subscript for the permeability of vacuum $\mu_{0}$, and other common scientific constants, is zero with subscript formatting, not a lowercase letter ``o''.
%\item In American English, commas, semicolons, periods, question and exclamation marks are located within quotation marks only when a complete thought or name is cited, such as a title or full quotation. When quotation marks are used, instead of a bold or italic typeface, to highlight a word or phrase, punctuation should appear outside of the quotation marks. A parenthetical phrase or statement at the end of a sentence is punctuated outside of the closing parenthesis (like this). (A parenthetical sentence is punctuated within the parentheses.)
%\item A graph within a graph is an ``inset'', not an ``insert''. The word alternatively is preferred to the word ``alternately'' (unless you really mean something that alternates).
%\item Do not use the word ``essentially'' to mean ``approximately'' or ``effectively''.
%\item In your paper title, if the words ``that uses'' can accurately replace the word ``using'', capitalize the ``u''; if not, keep using lower-cased.
%\item Be aware of the different meanings of the homophones ``affect'' and ``effect'', ``complement'' and ``compliment'', ``discreet'' and ``discrete'', ``principal'' and ``principle''.
%\item Do not confuse ``imply'' and ``infer''.
%\item The prefix ``non'' is not a word; it should be joined to the word it modifies, usually without a hyphen.
%\item There is no period after the ``et'' in the Latin abbreviation ``et al.''.
%\item The abbreviation ``i.e.'' means ``that is'', and the abbreviation ``e.g.'' means ``for example''.
%\end{itemize}
%An excellent style manual for science writers is \cite{b7}.
%
%\subsection{Authors and Affiliations}
%\textbf{The class file is designed for, but not limited to, six authors.} A 
%minimum of one author is required for all conference articles. Author names 
%should be listed starting from left to right and then moving down to the 
%next line. This is the author sequence that will be used in future citations 
%and by indexing services. Names should not be listed in columns nor group by 
%affiliation. Please keep your affiliations as succinct as possible (for 
%example, do not differentiate among departments of the same organization).
%
%\subsection{Identify the Headings}
%Headings, or heads, are organizational devices that guide the reader through 
%your paper. There are two types: component heads and text heads.
%
%Component heads identify the different components of your paper and are not 
%topically subordinate to each other. Examples include Acknowledgments and 
%References and, for these, the correct style to use is ``Heading 5''. Use 
%``figure caption'' for your Figure captions, and ``table head'' for your 
%table title. Run-in heads, such as ``Abstract'', will require you to apply a 
%style (in this case, italic) in addition to the style provided by the drop 
%down menu to differentiate the head from the text.
%
%Text heads organize the topics on a relational, hierarchical basis. For 
%example, the paper title is the primary text head because all subsequent 
%material relates and elaborates on this one topic. If there are two or more 
%sub-topics, the next level head (uppercase Roman numerals) should be used 
%and, conversely, if there are not at least two sub-topics, then no subheads 
%should be introduced.
%
%\subsection{Figures and Tables}
%\paragraph{Positioning Figures and Tables} Place figures and tables at the top and 
%bottom of columns. Avoid placing them in the middle of columns. Large 
%figures and tables may span across both columns. Figure captions should be 
%below the figures; table heads should appear above the tables. Insert 
%figures and tables after they are cited in the text. Use the abbreviation 
%``Fig.~\ref{fig}'', even at the beginning of a sentence.
%
%\begin{table}[htbp]
%\caption{Table Type Styles}
%\begin{center}
%\begin{tabular}{|c|c|c|c|}
%\hline
%\textbf{Table}&\multicolumn{3}{|c|}{\textbf{Table Column Head}} \\
%\cline{2-4} 
%\textbf{Head} & \textbf{\textit{Table column subhead}}& \textbf{\textit{Subhead}}& \textbf{\textit{Subhead}} \\
%\hline
%copy& More table copy$^{\mathrm{a}}$& &  \\
%\hline
%\multicolumn{4}{l}{$^{\mathrm{a}}$Sample of a Table footnote.}
%\end{tabular}
%\label{tab1}
%\end{center}
%\end{table}
%
%\begin{figure}[htbp]
%\centerline{\includegraphics{fig1.png}}
%\caption{Example of a figure caption.}
%\label{fig}
%\end{figure}
%
%Figure Labels: Use 8 point Times New Roman for Figure labels. Use words 
%rather than symbols or abbreviations when writing Figure axis labels to 
%avoid confusing the reader. As an example, write the quantity 
%``Magnetization'', or ``Magnetization, M'', not just ``M''. If including 
%units in the label, present them within parentheses. Do not label axes only 
%with units. In the example, write ``Magnetization (A/m)'' or ``Magnetization 
%\{A[m(1)]\}'', not just ``A/m''. Do not label axes with a ratio of 
%quantities and units. For example, write ``Temperature (K)'', not 
%``Temperature/K''.
%
%\section*{Acknowledgment}
%
%The preferred spelling of the word ``acknowledgment'' in America is without 
%an ``e'' after the ``g''. Avoid the stilted expression ``one of us (R. B. 
%G.) thanks $\ldots$''. Instead, try ``R. B. G. thanks$\ldots$''. Put sponsor 
%acknowledgments in the unnumbered footnote on the first page.

\bibliography{references.bib}{}
\bibliographystyle{IEEEtran}

\end{document}

### 2021-03-11 paper/main.tex
introduction

@@
 \section{Introduction}
-Nowadays, keeping track of the domestic energy usage is a common scenario in order to know how much is the real-time watt consumption. 
-Anyway, in the most cases there is a sensor connected to the main safety switch giving the total energy consumption.
-Instead, our scenario is more accurate since we have a energy sensor for each plug connected to 220V line.
-In the following paragraphs, we are presenting our \textit{proof of concept} (POC) which consists of three main parts: the smart plugs, the main server and the web interface.
+Nowadays, keeping track of the domestic energy usage is a common scenario in domotic applications that aim to monitor the real-time watt consumption of home appliances.
+In most cases the solution is a sensor connected to the main safety switch yielding the total energy consumption.
+Our approach, to get more detailed information and to have control on the use of power by the appliances, is to have an energy sensor for each plug connected to the 220V line.
+In the following paragraphs, we present our \textit{proof of concept} (POC) which, functionally, consists of three main components: the smart plugs, the main server and the web interface.
 In our POC, we have modified the architecture described in \cite{8110428} obtaining a specific low-energy consume-driven infrastructure.
-This latter consists of three main parts: the smart plugs, a central processing unit and the web interface.
-These devices are connected to the a wireless router, so is home scenario described below.
-It's a simple idea: let's suppose for example to plug both the dishwasher and the washing machine to two different smart plugs, and the user set up the max power consumption available for his house.
-On the first use of home appliances, a default value is choose in order to avoid blackout, and then we register the maximum power usage for each appliance.
-The user could turn on only the devices with a power consumption lower than the available watts.
-This is simple idea opens to possible different security issues, implementations and improvements that will be discussed in the challenges section.
+This consists of: the smart plugs, a central processing unit (for the main server) and a device (for the web interface).
+In a home scenario these devices are connected to the home wireless router.
+The communication between smart plugs and server occur over UDP with a simple form of reliability implemented at the application level.
+Let's now consider a use case example: the user sets the maximum power consumption possible in the home and then turns on two appliances.
+When this happens for the first time the system decides, based on the type of appliance connected, a default value for the maximum power usage of the appliance.
+This value is then updated to reflect the real maximum power usage of the appliance.
+Now that the system is running and some appliances are turned on, the user will be able to switch on only the appliances that consume less then the available power.
+Our POC covers this use case and shows that such a system can be practical and useful and that the traffic generated isn't enough to sensibly worsen the performances of the typical home WLAN.
+To summarize, the system keeps the power usage from reaching the maximum limit set by the user by forbidding the power on of appliances that consume more then the available power.
+It also gives granular information about the devices consumption and allows the user to turn on or off appliances remotely (via web interface).
+Aside from the main use case, in the age of climate awareness, such a system could be interesting to an environmentally conscious user that can monitor the power usage of appliances but also could set the maximum power consumption to be lower then the real one in order to use less power or save money.
 

### 2021-03-11 paper/main.tex
more intro, abstract

@@
 \begin{abstract}
-This document is a model and instructions for \LaTeX.
-This and the IEEEtran.cls file define the components of your paper [title, text, heads, etc.]. *CRITICAL: Do Not Use Symbols, Special Characters, Footnotes, 
-or Math in Paper Title or Abstract.
+This document describes a prototype of domotic smart plugs.
+The system developed includes the smart plugs, a server and a web interface that allow the user to monitor the power consumption of each individual appliance connected and power them on and off remotely.
+Furthermore the system, provided that its settings are correct, keep the user from turning on enough appliances to trigger the circuit breaker.
+The prototype has been developed keeping in mind issues of power consumption and reliability of communication between components of the system while keeping the traffic light.
 \end{abstract}
@@
 The communication between smart plugs and server occur over UDP with a simple form of reliability implemented at the application level.
+The smart plugs have been prototyped using Arduino and the server has been written in Java.
 Let's now consider a use case example: the user sets the maximum power consumption possible in the home and then turns on two appliances.

### 2021-03-11 paper/main.tex
starting general architecture

@@
 \begin{IEEEkeywords}
-component, formatting, style, styling, insert
+Domotic plugs; ADD MORE HERE
 \end{IEEEkeywords}
@@
 \section{General architecture}
-As we already said, the architecture implemented is different from the usually provided by this type of system, also because the modern infrastructure relies on cloud computing or external services.
-Our implementation do not share information about the user, and keeps all the data in the main server, eventually providing the possibility to accessed from outside.
-Anyway, in this case is not true that a cloud-computing is better, even if is more scalable, if there is no power available at home, the plugs will not be managed correctly either in a decentralized infrastructure.
-Even worse in a cloud based system, the plugs could not work properly, if there is no internet connection.
+The architecture implemented differs from the most common architectures used in this scenario in two major aspects, first most homes don't have this kind of system even in place, instead a circuit breaker triggers for safety reasons when too much power is being consumed.
+Second, when a similar system is used it usually relies on cloud computing or external services.
+In contrast our system offers the functionalities already described and both computing and data storage are done locally.
+This can be an advantage in terms of both privacy and security.
+Furthermore, this is in advantage in terms of reliability: our system doesn't need an internet connection to properly work, instead it just needs a working WLAN.
+However, while this aspect is significant, the development of the prototype hasn't focused on the security aspects and security issues will be discussed in the appropriate section.
+The architecture of the system is such that if need be it can be easily modified to use third party services.
 \par After describing some architectural design aspects,%

### 2021-03-11 paper/main.tex
general

@@
 \begin{IEEEkeywords}
-Domotic plugs; ADD MORE HERE
+Domotic plugs; Reliable UDP; ADD MORE
 \end{IEEEkeywords}
@@
 Furthermore, this is in advantage in terms of reliability: our system doesn't need an internet connection to properly work, instead it just needs a working WLAN.
-However, while this aspect is significant, the development of the prototype hasn't focused on the security aspects and security issues will be discussed in the appropriate section.
+However, while this aspect is significant, the development of the prototype hasn't focused on the security aspects and some issues will be discussed in the appropriate section.
 The architecture of the system is such that if need be it can be easily modified to use third party services.
+
+The general architecture has 3 main components: the smart plugs, an UDP server, the web interface.
+
+The smart plugs have been prototyped using Arduino. The module drives a sensor, needed to gather data on the power consumption and communicates with the UDP server 
 \par After describing some architectural design aspects,%

### 2021-03-13 paper/main.tex
summary

@@
 In a home scenario these devices are connected to the home wireless router.
-The communication between smart plugs and server occur over UDP with a simple form of reliability implemented at the application level.
+The communication between smart plugs and server occur over UDP with a simple form of reliability implemented at the application level, and tested using Wireshark \cite{wireshark}.
 The smart plugs have been prototyped using Arduino and the server has been written in Java.
@@
 The smart plugs have been prototyped using Arduino. The module drives a sensor, needed to gather data on the power consumption and communicates with the UDP server 
-\par After describing some architectural design aspects,%
+\par After describing some architectural design aspects,
+\subsection{Smart plugs}\label{SP}
+\subsection{Server}\label{SVR}
+\subsection{Web interface}\label{WI}
+
+\section{System results}
+\section{Consumption}
+%Qui mettiamo workflow generale con immagine algoritmo
+
+%
 %\subsection{Maintaining the Integrity of the Specifications}

### 2021-03-13 paper/main.tex
restructuring introduction

@@
 should not be used}
-\thanks{Identify applicable funding agency here. If none, delete this.}
+%\thanks{Identify applicable funding agency here. If none, delete this.}
 }
@@
 \begin{IEEEkeywords}
-Domotic plugs; Reliable UDP; ADD MORE
+Domotic plugs; Reliable UDP;
 \end{IEEEkeywords}
@@
 \section{Introduction}
-Nowadays, keeping track of the domestic energy usage is a common scenario in domotic applications that aim to monitor the real-time watt consumption of home appliances.
-In most cases the solution is a sensor connected to the main safety switch yielding the total energy consumption.
-Our approach, to get more detailed information and to have control on the use of power by the appliances, is to have an energy sensor for each plug connected to the 220V line.
-In the following paragraphs, we present our \textit{proof of concept} (POC) which, functionally, consists of three main components: the smart plugs, the main server and the web interface.
-In our POC, we have modified the architecture described in \cite{8110428} obtaining a specific low-energy consume-driven infrastructure.
-This consists of: the smart plugs, a central processing unit (for the main server) and a device (for the web interface).
-In a home scenario these devices are connected to the home wireless router.
-The communication between smart plugs and server occur over UDP with a simple form of reliability implemented at the application level, and tested using Wireshark \cite{wireshark}.
+Nowadays, keeping track of domestic energy usage is a common scenario in domotic applications that aim to monitor the real-time watt consumption of home appliances.
+In most cases, the solution is a sensor connected to the main safety switch yielding the total energy consumption.
+Our approach, to get more detailed information and to have control over the use of power by the appliances, is to have an energy sensor for each plug connected to the 220V line.
+In the following paragraphs, we present our \textit{proof of concept} (POC) which, functionally, consists of three main components: the smart plugs, the server, and the web interface.
+In our POC, we have modified the architecture described in \cite{8110428} obtaining a specific low-energy consumption-driven infrastructure.
+This consists of the smart plugs, a computer (for the server), and a device (for the web interface).
+In a home scenario, these devices are connected to the home wireless router.
+The communication between smart plugs and server occur over UDP with a simple form of reliability implemented at the application level and tested using Wireshark \cite{wireshark}.
+The architecture implemented differs from the most common ones in two major aspects: first, most homes aren't equipped with this kind of system, instead, a circuit breaker triggers for safety reasons when too much power is being consumed.
+Second, when a similar system is used it usually relies on cloud computing or external services.
+In contrast, our system offers the functionalities already described and both computing and data storage are performed locally.
+This can be an advantage in terms of both privacy and security.
+Furthermore, this is an advantage in terms of reliability: our system doesn't need an internet connection to work properly, instead, it just needs a working WLAN.
+However, while this aspect is significant, the development of the prototype hasn't focused on the security aspects and some issues will be discussed in the appropriate section.
+The architecture of the system is such that if need be it can be easily modified to use third-party services.
 The smart plugs have been prototyped using Arduino and the server has been written in Java.
@@
 This value is then updated to reflect the real maximum power usage of the appliance.
-Now that the system is running and some appliances are turned on, the user will be able to switch on only the appliances that consume less then the available power.
+Now that the system is running and some appliances are turned on, the user will be able to switch on only the appliances that consume less than the available power.
 Our POC covers this use case and shows that such a system can be practical and useful and that the traffic generated isn't enough to sensibly worsen the performances of the typical home WLAN.
-To summarize, the system keeps the power usage from reaching the maximum limit set by the user by forbidding the power on of appliances that consume more then the available power.
-It also gives granular information about the devices consumption and allows the user to turn on or off appliances remotely (via web interface).
-Aside from the main use case, in the age of climate awareness, such a system could be interesting to an environmentally conscious user that can monitor the power usage of appliances but also could set the maximum power consumption to be lower then the real one in order to use less power or save money.
+To summarize, the system keeps the power usage from reaching the maximum limit set by the user by forbidding the power-on of appliances that consume more than the available power.
+It also gives granular information about the energy consumption of the device and allows the user to turn on or off appliances remotely (via web interface).
+Aside from the main use case, in the age of climate awareness, such a system could be interesting to an environmentally conscious user that can monitor the power usage of appliances but also could set the maximum power consumption to be lower than the real one to use less power or save money.
 
 \section{General architecture}
-The architecture implemented differs from the most common architectures used in this scenario in two major aspects, first most homes don't have this kind of system even in place, instead a circuit breaker triggers for safety reasons when too much power is being consumed.
-Second, when a similar system is used it usually relies on cloud computing or external services.
-In contrast our system offers the functionalities already described and both computing and data storage are done locally.
-This can be an advantage in terms of both privacy and security.
-Furthermore, this is in advantage in terms of reliability: our system doesn't need an internet connection to properly work, instead it just needs a working WLAN.
-However, while this aspect is significant, the development of the prototype hasn't focused on the security aspects and some issues will be discussed in the appropriate section.
-The architecture of the system is such that if need be it can be easily modified to use third party services.
-
-The general architecture has 3 main components: the smart plugs, an UDP server, the web interface.
+The general architecture has 3 main components: the smart plugs, the server, and the web interface.
 

### 2021-03-13 paper/main.tex
correction in abstract

@@
 This document describes a prototype of domotic smart plugs.
-The system developed includes the smart plugs, a server and a web interface that allow the user to monitor the power consumption of each individual appliance connected and power them on and off remotely.
-Furthermore the system, provided that its settings are correct, keep the user from turning on enough appliances to trigger the circuit breaker.
+The system developed includes the smart plugs, a server, and a web interface that allow the user to monitor the power consumption of each individual appliance connected and power them on and off remotely.
+Furthermore, the system, provided that its settings are correct, keeps the user from turning on enough appliances to trigger the circuit breaker.
 The prototype has been developed keeping in mind issues of power consumption and reliability of communication between components of the system while keeping the traffic light.
@@
 In a home scenario, these devices are connected to the home wireless router.
-The communication between smart plugs and server occur over UDP with a simple form of reliability implemented at the application level and tested using Wireshark \cite{wireshark}.
+The communication between smart plugs and server occurs over UDP with a simple form of reliability implemented at the application level and tested using Wireshark \cite{wireshark}.
 The architecture implemented differs from the most common ones in two major aspects: first, most homes aren't equipped with this kind of system, instead, a circuit breaker triggers for safety reasons when too much power is being consumed.

### 2021-03-13 paper/main.tex
Aggiunto smart plug

@@
+% !TeX spellcheck = en_US
 \documentclass[conference]{IEEEtran}
@@
 
-\title{Conference Paper Title*\\
-{\footnotesize \textsuperscript{*}Note: Sub-titles are not captured in Xplore and
-should not be used}
+\title{Wireless smart monitoring energy system: a proof of concept}
+{
 %\thanks{Identify applicable funding agency here. If none, delete this.}
@@
 
-\author{\IEEEauthorblockN{1\textsuperscript{st} Given Name Surname}
-\IEEEauthorblockA{\textit{dept. name of organization (of Aff.)} \\
-\textit{name of organization (of Aff.)}\\
-City, Country \\
-email address or ORCID}
+\author{
+\IEEEauthorblockN{Marco Costantino}
+\IEEEauthorblockA{\textit{Department of Mathematics} \\
+\textit{University of Padova}\\
+Padova, Italia \\
+marco.costantino1@studenti.unipd.it}
 \and
-\IEEEauthorblockN{2\textsuperscript{nd} Given Name Surname}
-\IEEEauthorblockA{\textit{dept. name of organization (of Aff.)} \\
-\textit{name of organization (of Aff.)}\\
-City, Country \\
-email address or ORCID}
-\and
-\IEEEauthorblockN{3\textsuperscript{rd} Given Name Surname}
-\IEEEauthorblockA{\textit{dept. name of organization (of Aff.)} \\
-\textit{name of organization (of Aff.)}\\
-City, Country \\
-email address or ORCID}
-\and
-\IEEEauthorblockN{4\textsuperscript{th} Given Name Surname}
-\IEEEauthorblockA{\textit{dept. name of organization (of Aff.)} \\
-\textit{name of organization (of Aff.)}\\
-City, Country \\
-email address or ORCID}
-\and
-\IEEEauthorblockN{5\textsuperscript{th} Given Name Surname}
-\IEEEauthorblockA{\textit{dept. name of organization (of Aff.)} \\
-\textit{name of organization (of Aff.)}\\
-City, Country \\
-email address or ORCID}
-\and
-\IEEEauthorblockN{6\textsuperscript{th} Given Name Surname}
-\IEEEauthorblockA{\textit{dept. name of organization (of Aff.)} \\
-\textit{name of organization (of Aff.)}\\
-City, Country \\
-email address or ORCID}
+\IEEEauthorblockN{Francesco Magarotto}
+\IEEEauthorblockA{\textit{Department of Mathematics} \\
+\textit{University of Padova}\\
+Padova, Italy \\
+francesco.magarotto@studenti.unipd.it}
 }
@@
 \subsection{Smart plugs}\label{SP}
+The smart plugs is a small hardware plug which consists of a WeMos D1 R2 board, a 220v relay that can be controlled using 5 volts digital signals, and coil connected to a PZEM-004T sensor which provides the readings to WeMos through its digital pins.
+The connection scheme is represented in Figure~\ref{fig:pcbschema}, and has a cost about €25, so it is not so expensive. 
+The WeMos D1 R2 board is equipped with a wireless module working at 2.4GHz called EPS 8266 and the wireless connection settings are hard coded in the software, since to store a configuration file an SD module and an SD card are needed.
+The board is programmed in C/C++ using Arduino IDE and uses an UDP library to create the packets which data are serialized using the JSON format.
+In every Arduino-like board, there is a function which allow our program to wait for UDP package arrivals from the server, affecting the relay status.
+Another thread, once the board has recognized and registered the server, sends update periodically if there is a variation greater than the 10\% of the energy consumption.
+\begin{figure}[htbp]
+	\centering
+	\includegraphics[width=\linewidth]{assets/pcb_schema}
+	\caption{Electric schema of the wireless smart plug}
+	\label{fig:pcbschema}
+\end{figure}
+
 \subsection{Server}\label{SVR}

### 2021-03-14 paper/main.tex
Aggiunte parti

@@
 The board is programmed in C/C++ using Arduino IDE and uses an UDP library to create the packets which data are serialized using the JSON format.
-In every Arduino-like board, there is a function which allow our program to wait for UDP package arrivals from the server, affecting the relay status.
+In every Arduino-like board, there is a function which allows our program to wait for UDP package arrivals from the server, affecting the relay status.
 Another thread, once the board has recognized and registered the server, sends update periodically if there is a variation greater than the 10\% of the energy consumption.
+Firstly, smart plugs wait for an \textit{INIT message}, sent by the server via broadcast.
+Once the packet has been received, each plug saves the information about the server and is not replying to this type of messages for a certain amount of type, or until a hard reset is performed.
+Then, the plug starts to send \textit{UPDATE messages} to inform the server about a energy consumption variation. To do so, a thread keeps watch over the readings provided by the PZEM sensor.
+In order to switch correctly the relay, the board waits for \textit{ON/OFF messages} from the server.
+After those requests has been received correctly, the correct action is performed and then a \textit{ACK message} is sent to inform the server about the successful receipt of the command.
 \begin{figure}[htbp]

### 2021-03-14 paper/main.tex
client

@@
 \subsection{Web interface}\label{WI}
-
+The web interface is written in React using Bootstrap and exposes a way to interact with the server getting 
+a real-time power consumption for each device and managing the connected devices.
+It performs some to HTTP, so over TCP, to the API exposed by the server through the servlet, performing polling calls.
+The GUI as can we see in Figure \textbf{put figure here} presents a switch where the user can turn off or on the plug.
+If there is not enough energy available to turn on a device, the switch will be displayed as disabled in order to avoid blackout.
 \section{System results}

### 2021-03-14 paper/main.tex
server section of the paper

@@
 \subsection{Server}\label{SVR}
+The server uses Tomcat and has been developed in Java 1.8 using Maven. It has the following responsibilities:
+\begin{itemize}
+	\item It periodically broadcasts \textit{INIT messages} to let the plugs know its address;
+	\item It listens for connections and updates from the plugs;
+	\item It waits for acknowledgments from the plugs and, in case they are not received, it retransmits the lost packets;
+	\item It exposes servlets to let the web interface get information about the plugs and send \textit{ON/OFF messages}.
+\end{itemize}
+The periodic actions, namely, sending the \textit{INIT message} and retransmitting those that are lost, are implemented as extensions of \textit{Guava's AbstractScheduledService} which allows performing of these at constant intervals.
+Another thread waits and manages the plugs' responses.
+When a plug responds to the \textit{INIT message} the server will register its information and estimate the max power consumption for the appliance connected to the plug.
+This value is simply based on average values for the given appliance type as found on Google.
+When a plug sends an \textit{UPDATE message} the server will update its registered information, most important: the current energy consumption and the max energy consumption.
+Finally, the server waits for the acknowledgments of previously sent messages.
+These messages are kept with a timestamp until an acknowledgment with the same timestamp is received.
+If a configurable number of seconds elapses before this happens the packet will be sent again.
+The servlets simply allow the web interface to get the server's information about the plugs (the type of appliance connected, the current energy consumption, and more) and to turn ON or OFF any given plug.
+In this last case, a packet will be sent by the server and for it the server will wait for an acknowledgment.
+The information about the plugs saved by the server is kept as a \textit{thread-safe hashmap}.
+Some of this information, such as the IP address of the plugs, the type of appliance connected and the max power consumption is also saved in a \textit{XML file} to avoid loosing it in case of a server malfunction or restart.
 \subsection{Web interface}\label{WI}

### 2021-03-14 paper/main.tex
minor correction

@@
 \textit{University of Padova}\\
-Padova, Italia \\
-marco.costantino1@studenti.unipd.it}
+Padova, Italy \\
+marco.costantino@studenti.unipd.it}
 \and
@@
 \subsection{Smart plugs}\label{SP}
-The smart plugs is a small hardware plug which consists of a WeMos D1 R2 board, a 220v relay that can be controlled using 5 volts digital signals, and coil connected to a PZEM-004T sensor which provides the readings to WeMos through its digital pins.
+The smart plug is a small power plug which consists of a WeMos D1 R2 board, a 220v relay that can be controlled using 5 volts digital signals, and a coil connected to a PZEM-004T sensor which provides the readings to WeMos through its digital pins.
 The connection scheme is represented in Figure~\ref{fig:pcbschema}, and has a cost about €25, so it is not so expensive. 
-The WeMos D1 R2 board is equipped with a wireless module working at 2.4GHz called EPS 8266 and the wireless connection settings are hard coded in the software, since to store a configuration file an SD module and an SD card are needed.
-The board is programmed in C/C++ using Arduino IDE and uses an UDP library to create the packets which data are serialized using the JSON format.
+The WeMos D1 R2 board is equipped with a EPS 8266 wireless module operating at 2.4GHz.
+The connection settings are hardcoded in the software because storing it would require an SD module and an SD card.
+The board is programmed in C/C++ using Arduino IDE and uses the JSON format to serialize the data that will be sent, using a UDP library, to the server.
 In every Arduino-like board, there is a function which allows our program to wait for UDP package arrivals from the server, affecting the relay status.
-Another thread, once the board has recognized and registered the server, sends update periodically if there is a variation greater than the 10\% of the energy consumption.
-Firstly, smart plugs wait for an \textit{INIT message}, sent by the server via broadcast.
+Another thread, once the board has recognized and registered the server, sends updates periodically if there is a variation greater than the 10\% of the energy consumption.
+First, smart plugs wait for an \textit{INIT message}, sent by the server via broadcast.
 Once the packet has been received, each plug saves the information about the server and is not replying to this type of messages for a certain amount of type, or until a hard reset is performed.
-Then, the plug starts to send \textit{UPDATE messages} to inform the server about a energy consumption variation. To do so, a thread keeps watch over the readings provided by the PZEM sensor.
+Then, the plug starts to send \textit{UPDATE messages} to inform the server about energy consumption variation. To do so, a thread keeps watch over the readings provided by the PZEM sensor.
 In order to switch correctly the relay, the board waits for \textit{ON/OFF messages} from the server.
-After those requests has been received correctly, the correct action is performed and then a \textit{ACK message} is sent to inform the server about the successful receipt of the command.
+After those requests have been received correctly, the correct action is performed and then an \textit{ACK message} is sent to inform the server about the successful receipt of the command.
 \begin{figure}[htbp]
@@
 \subsection{Web interface}\label{WI}
-The web interface is written in React using Bootstrap and exposes a way to interact with the server getting 
-a real-time power consumption for each device and managing the connected devices.
+The web interface is written in React using Bootstrap and exposes a way to interact with the server to get 
+the real-time power consumption for each plug and managing the connected devices.
 It performs some to HTTP, so over TCP, to the API exposed by the server through the servlet, performing polling calls.
-The GUI as can we see in Figure \textbf{put figure here} presents a switch where the user can turn off or on the plug.
-If there is not enough energy available to turn on a device, the switch will be displayed as disabled in order to avoid blackout.
+The GUI shown in Figure \textbf{put figure here} presents a switch where the user can turn on or off the plug.
+If there is not enough energy available to turn on a device, the switch will be displayed as disabled in order to avoid a blackout.
 \section{System results}

### 2021-03-14 paper/main.tex
added architecture figure

@@
 The general architecture has 3 main components: the smart plugs, the server, and the web interface.
+The smart plugs have been prototyped using Arduino.
+The server has been developed in Java and the web interface is written in React.
+The rundown of what each part does is as follows: Arduino drives a sensor that gathers data on the power consumption of the plug and communicates with the UDP server that keeps track of the plugs and their energy consumption.
+The web interface uses an API exposed by the server to let the user see and control the status of each plug.
+\begin{figure}[htbp]
+	\centering
+	\includegraphics[width=\linewidth]{assets/architecture_schema}
+	\caption{General architecture of the system}
+	\label{fig:architecture_schema}
+\end{figure}
 
-The smart plugs have been prototyped using Arduino. The module drives a sensor, needed to gather data on the power consumption and communicates with the UDP server 
-\par After describing some architectural design aspects,
 \subsection{Smart plugs}\label{SP}

### 2021-03-15 paper/main.tex
rewording server intro
Summary

@@
 \section{General architecture}
-The general architecture has 3 main components: the smart plugs, the server, and the web interface.
+The general architecture has three main components: the smart plugs, the server, and the web interface.
 The smart plugs have been prototyped using Arduino.
@@
 The smart plug is a small power plug which consists of a WeMos D1 R2 board, a 220v relay that can be controlled using 5 volts digital signals, and a coil connected to a PZEM-004T sensor which provides the readings to WeMos through its digital pins.
-The connection scheme is represented in Figure~\ref{fig:pcbschema}, and has a cost about €25, so it is not so expensive. 
+The connection scheme is represented in Figure~\ref{fig:pcbschema}, and has a cost about €15, so it is not so expensive. 
 The WeMos D1 R2 board is equipped with a EPS 8266 wireless module operating at 2.4GHz.
@@
 After those requests have been received correctly, the correct action is performed and then an \textit{ACK message} is sent to inform the server about the successful receipt of the command.
+We also used a different board called NodeMcu V3 in order to simulate a plug to get a real traffic scenario with at least two plugs.
+Since, NodeMcu V3 is not connected to a PZEM module, the power consumption readings are random values.
 \begin{figure}[htbp]
@@
 	\label{fig:pcbschema}
+\end{figure}
+\begin{figure}
+	\centering
+	\includegraphics[width=0.7\linewidth]{assets/IMG_5348}
+	\caption{Proof of concept of our smart plug}
+	\label{fig:img5348}
 \end{figure}
@@
 It performs some to HTTP, so over TCP, to the API exposed by the server through the servlet, performing polling calls.
-The GUI shown in Figure \textbf{put figure here} presents a switch where the user can turn on or off the plug.
+The GUI shown in Figure~\ref{fig:simulatedwebapp} presents a switch where the user can turn on or off the plug.
 If there is not enough energy available to turn on a device, the switch will be displayed as disabled in order to avoid a blackout.
+\begin{figure}[htbp]
+	\centering
+	\includegraphics[width=0.7\linewidth]{assets/simulated_webapp}
+	\caption{Web interface used to control the whole system}
+	\label{fig:simulatedwebapp}
+\end{figure}
+
 \section{System results}

### 2021-03-15 paper/main.tex
server refactor, methods

@@
 \subsection{Server}\label{SVR}
-The server uses Tomcat and has been developed in Java 1.8 using Maven. It has the following responsibilities:
-\begin{itemize}
-	\item It periodically broadcasts \textit{INIT messages} to let the plugs know its address;
-	\item It listens for connections and updates from the plugs;
-	\item It waits for acknowledgments from the plugs and, in case they are not received, it retransmits the lost packets;
-	\item It exposes servlets to let the web interface get information about the plugs and send \textit{ON/OFF messages}.
-\end{itemize}
+The server has been developed in Java 8 and managed using Maven.
+Tomcat is implemented to expose the servlet API.
+The server has the following responsibilities: to periodically broadcasts \textit{INIT messages} to let the plugs know its address; It listens for connections and updates from the plugs; it waits for acknowledgments from the plugs and, in case they are not received, it retransmits the lost packets; it exposes servlets to let the web interface get information about the plugs and send \textit{ON/OFF messages}.
 The periodic actions, namely, sending the \textit{INIT message} and retransmitting those that are lost, are implemented as extensions of \textit{Guava's AbstractScheduledService} which allows performing of these at constant intervals.
@@
 
+\section{Methods}
+Throughout the development, the communication between server and the plug has been simulated and tested using PacketSender which is a tool that allow to send a configurable packet through the network.
+To check the system's traffic and the correct handling of acknowledgments, we used PacketSender to simulate the traffic generated by the plug but not the acknowledgments and Wireshark to filter the traffic by port and type and check the correct retransmition of packets by the server.
+Finally the entire system as been tested to check the correct transmission of acknowledgments by the plugs.
 \section{System results}

### 2021-03-15 paper/main.tex
server logic image

@@
 If a configurable number of seconds elapses before this happens the packet will be sent again.
+\begin{figure}
+	\centering
+	\includegraphics[width=0.7\linewidth]{assets/server_logic}
+	\caption{Overview of server's logic for handling packets received by the plugs}
+	\label{fig:server_logic}
+\end{figure}
 The servlets simply allow the web interface to get the server's information about the plugs (the type of appliance connected, the current energy consumption, and more) and to turn ON or OFF any given plug.
@@
 Some of this information, such as the IP address of the plugs, the type of appliance connected and the max power consumption is also saved in a \textit{XML file} to avoid loosing it in case of a server malfunction or restart.
+
 \subsection{Web interface}\label{WI}
@@
 Finally the entire system as been tested to check the correct transmission of acknowledgments by the plugs.
+
 \section{System results}

### 2021-03-15 paper/main.tex
added sections for the packets

--- 2021-03-15 paper/main.tex
@@
 \usepackage{xcolor}
+\usepackage{spverbatim}
 \def\BibTeX{{\rm B\kern-.05em{\sc i\kern-.025em b}\kern-.08em
@@
 The smart plug is a small power plug which consists of a WeMos D1 R2 board, a 220v relay that can be controlled using 5 volts digital signals, and a coil connected to a PZEM-004T sensor which provides the readings to WeMos through its digital pins.
-The connection scheme is represented in Figure~\ref{fig:pcbschema}, and has a cost about €15, so it is not so expensive. 
+The connection scheme is represented in Figure~\ref{fig:pcbschema}, and has a cost about €15, so it is not that expensive. 
 The WeMos D1 R2 board is equipped with a EPS 8266 wireless module operating at 2.4GHz.
@@
 The board is programmed in C/C++ using Arduino IDE and uses the JSON format to serialize the data that will be sent, using a UDP library, to the server.
-In every Arduino-like board, there is a function which allows our program to wait for UDP package arrivals from the server, affecting the relay status.
+In every Arduino-like board, there is a function that allows our program to wait for UDP package arrivals from the server, affecting the relay status.
 Another thread, once the board has recognized and registered the server, sends updates periodically if there is a variation greater than the 10\% of the energy consumption.
@@
 Then, the plug starts to send \textit{UPDATE messages} to inform the server about energy consumption variation. To do so, a thread keeps watch over the readings provided by the PZEM sensor.
+The content of the packets is first defined as a JSON object and then serialized to the bytes that are the payload of the UDP packet.
+All of these packets have a field in common: \verb|act| this field can have as values:
+\begin{itemize}
+	\item \begin{spverbatim}"INIT"\end{spverbatim} when responding to the server's INIT packet;
+	\item \begin{spverbatim}"UPDATE"\end{spverbatim} when sending an update to the server;
+	\item \begin{spverbatim}"ACK"\end{spverbatim} when sending an acknowledgment to the server.
+\end{itemize}
+The \verb|"INIT"| packet contains three more fields:
+\begin{itemize}
+	\item \begin{spverbatim}"type"\end{spverbatim} indicates the type of appliance plugged;
+	\item \begin{spverbatim}"max_power_usage"\end{spverbatim} indicates how many watts the appliance is expected to consume;
+	\item \begin{spverbatim}"sts"\end{spverbatim} indicates if the status of the relay, \verb|0| for off, \verb|1| for on.
+\end{itemize}
+The \verb|UPDATE| packet has a \verb|type| field too, and has a field \verb|active_power| that is a reading of the currently consumed watts.
+Finally, the \verb|ACK| packet has the \verb|sts| field too, and has a field \verb|timestamp| which value is taken from the same field in the packet the plug received from the server.
 In order to switch correctly the relay, the board waits for \textit{ON/OFF messages} from the server.
@@
 \subsection{Server}\label{SVR}
-The server uses Tomcat and has been developed in Java 1.8 using Maven. It has the following responsibilities:
+The server has been developed in Java 8 and managed using Maven.
+Tomcat is implemented to expose the servlet API.
+The server has the following responsibilities: to periodically broadcasts \textit{INIT packets} to let the plugs know its address; It listens for connections and updates from the plugs; it waits for acknowledgments from the plugs and, in case they are not received, it retransmits the lost packets; it exposes servlets to let the web interface get information about the plugs and send \textit{ON/OFF packets}.
+The periodic actions, namely, sending the \textit{INIT packet} and retransmitting those that are lost, are implemented as extensions of \textit{Guava's AbstractScheduledService} which allows performing of these at constant intervals.
+Another thread waits and manages the plugs' responses.
+When a plug responds to the \textit{INIT packet} the server will register its information and estimate the max power consumption for the appliance connected to the plug.
+This value is simply based on average values for the given appliance type as found on Google.
+When a plug sends an \textit{UPDATE packet} the server will update its registered information, most important: the current energy consumption and the max energy consumption.
+Finally, the server waits for the acknowledgments of previously sent packets.
+These packets contain a timestamp which is sent back by the plugs in the acknowledgments.
+The server also has a list of packets waiting for acknowledgment, in this way when the server receives an ACK it can discard the packet with the given timestamp.
+If a configurable number of seconds elapses before this happens the packet will be sent again.
+Like the plugs, the server first defines the content of the packets it sends as JSON objects.
+All the packets sent by the server have a field: \verb|act| this field can have as values:
 \begin{itemize}
-	\item It periodically broadcasts \textit{INIT messages} to let the plugs know its address;
-	\item It listens for connections and updates from the plugs;
-	\item It waits for acknowledgments from the plugs and, in case they are not received, it retransmits the lost packets;
-	\item It exposes servlets to let the web interface get information about the plugs and send \textit{ON/OFF messages}.
+	\item \begin{spverbatim}"INIT"\end{spverbatim} when broadcasting the INIT packet;
+	\item \begin{spverbatim}"ON"\end{spverbatim} when sending a plug the instruction to turn on;
+	\item \begin{spverbatim}"OFF"\end{spverbatim} when sending a plug the instruction to turn off.
 \end{itemize}
-The periodic actions, namely, sending the \textit{INIT message} and retransmitting those that are lost, are implemented as extensions of \textit{Guava's AbstractScheduledService} which allows performing of these at constant intervals.
-Another thread waits and manages the plugs' responses.
-When a plug responds to the \textit{INIT message} the server will register its information and estimate the max power consumption for the appliance connected to the plug.
-This value is simply based on average values for the given appliance type as found on Google.
-When a plug sends an \textit{UPDATE message} the server will update its registered information, most important: the current energy consumption and the max energy consumption.
-Finally, the server waits for the acknowledgments of previously sent messages.
-These messages are kept with a timestamp until an acknowledgment with the same timestamp is received.
-If a configurable number of seconds elapses before this happens the packet will be sent again.
-The servlets simply allow the web interface to get the server's information about the plugs (the type of appliance connected, the current energy consumption, and more) and to turn ON or OFF any given plug.
+\verb|ON| and \verb|OFF| packets also have a field \verb|timestamp| which contains a string representation of the long value returned by java's \verb|System.currentTimeMillis()|.  
+\begin{figure}
+	\centering
+	\includegraphics[width=\linewidth]{assets/server_logic}
+	\caption{Overview of server's logic for handling packets received by the plugs}
+	\label{fig:server_logic}
+\end{figure}
+The servlets simply allow the web interface to get the server's information about the plugs (the type of appliance connected, the current energy consumption, and more) and to turn on or off any given plug.
 In this last case, a packet will be sent by the server and for it the server will wait for an acknowledgment.
@@
 \end{figure}
+
+\section{Methods}
+Throughout the development, the communication between the server and the plug has been simulated and tested using PacketSender which is a tool that allows sending a configurable packet through the network.
+To check the system's traffic and the correct handling of acknowledgments, we used PacketSender to simulate the traffic generated by the plug but not the acknowledgments and Wireshark to filter the traffic by port and type and check the correct retransmission of packets by the server.
+Finally, the entire system has been tested to check the correct transmission of acknowledgments by the plugs.
 

### 2021-03-15 paper/main.tex
tiny fix
web interface mods

@@
 The servlets simply allow the web interface to get the server's information about the plugs (the type of appliance connected, the current energy consumption, and more) and to turn on or off any given plug.
-In this last case, a packet will be sent by the server and for it the server will wait for an acknowledgment.
+In this last case, a packet will be sent by the server and for it the server will wait an acknowledgment.
 The information about the plugs saved by the server is kept as a \textit{thread-safe hashmap}.
@@
 \subsection{Web interface}\label{WI}
-The web interface is written in React using Bootstrap and exposes a way to interact with the server to get 
-the real-time power consumption for each plug and managing the connected devices.
-It performs some to HTTP, so over TCP, to the API exposed by the server through the servlet, performing polling calls.
+The web interface is written in React using Bootstrap and exposes a way to interact with the server to get the real-time power consumption for each plug and managing the connected devices.
+The polling calls to the API exposed by the server through the servlets are performed over HTTP and thefore using the TCP protocol.
 The GUI shown in Figure~\ref{fig:simulatedwebapp} presents a switch where the user can turn on or off the plug.

### 2021-03-16 paper/main.tex
tiny fix
expanding on methods

@@
 \section{Methods}
-Throughout the development, the communication between the server and the plug has been simulated and tested using PacketSender which is a tool that allows sending a configurable packet through the network.
-To check the system's traffic and the correct handling of acknowledgments, we used PacketSender to simulate the traffic generated by the plug but not the acknowledgments and Wireshark to filter the traffic by port and type and check the correct retransmission of packets by the server.
+Throughout the development, the communication between the server and the plug has been simulated and tested using PacketSender.
+This tool allows the user to define the content of a packet in ASCII format, this is turned into bytes and sent to the specified address and port.
+For our tests, we specified the content of the packets by writing the JSON object in ASCII format, the type of packet (UDP), and the server's address and port.
+In particular, we tested the system's traffic and the correct handling of acknowledgments.
+To do this we used PacketSender to simulate the traffic generated by the plug but not the acknowledgments and Wireshark, a packet analyzer, to check the correct retransmission of packets by the server by first filtering the traffic by port and type.
 Finally, the entire system has been tested to check the correct transmission of acknowledgments by the plugs.
@@
 \section{System results}
+
 \section{Consumption}

### 2021-03-16 paper/main.tex
more on challenges, conclusions

@@
 \end{itemize}
-\verb|ON| and \verb|OFF| packets also have a field \verb|timestamp| which contains a string representation of the long value returned by java's \verb|System.currentTimeMillis()|.  
+\verb|ON| and \verb|OFF| packets also have a field \verb|timestamp| which contains a string representation of the timestamp.  
 \begin{figure}
@@
 %Qui mettiamo workflow generale con immagine algoritmo
+
+\section{Challenges}
+During the development, we found some issues outside the scope of this POC.
+Since the focus of the project wasn't on security we decided for ease of debugging to do not encrypt the packets exchanged between plugs and server.
+Also, we did not develop an authentication system to use the web interface.
+
+\section{Conclusions}
+In the current day and age, we have the opportunity to make smart the most mundane objects.
+Smart plugs can be used to monitor energy consumption, give control to the user, and help the user reach a maximum consumption goal.
+These plugs can reliably operate using the UDP protocol provided there are some reliability checks at the application level and can do it in a busy home WLAN where traffic can be both TCP and UDP.
 

### 2021-03-17 paper/main.tex
challenges

@@
 This tool allows the user to define the content of a packet in ASCII format, this is turned into bytes and sent to the specified address and port.
-For our tests, we specified the content of the packets by writing the JSON object in ASCII format, the type of packet (UDP), and the server's address and port.
-In particular, we tested the system's traffic and the correct handling of acknowledgments.
-To do this we used PacketSender to simulate the traffic generated by the plug but not the acknowledgments and Wireshark, a packet analyzer, to check the correct retransmission of packets by the server by first filtering the traffic by port and type.
+For our tests, we specified the content of the packets by writing the JSON object in ASCII format, the type of packet (UDP), and the server address and port.
+In particular, we tested the system traffic and the correct handling of acknowledgments.
+To do this we used PacketSender to simulate the traffic generated by the plug but not the acknowledgments and Wireshark, a packet analyzer, to check the correct re-transmission of packets by the server by first filtering the traffic by port and type.
 Finally, the entire system has been tested to check the correct transmission of acknowledgments by the plugs.
@@
 Since the focus of the project wasn't on security we decided for ease of debugging to do not encrypt the packets exchanged between plugs and server.
-Also, we did not develop an authentication system to use the web interface.
-
+The plugs configuration is hard-coded, for example the Wi-Fi SSID and password are stored as a char array in our C++ code.
+Since the EPS 8266 could switch to access point mode which means generate a new wireless network, a configuration procedure could be implemented.
+A device - such as a smartphone - could connect to the plug wireless network and send the SSID and password required by our home wireless settings.
+Those information should be stored in a persistent drive - as a micro SD card - and also, in order to not increase the POC complexity and keep the costs low, we did not implemented those procedures.
+Another challenge to face is the security issue, the information send from a plug to the server are completely clear, so there is no encryption implemented.
+A man-in-the-middle attack could intercept those packages and change their contents.
+An attackers could also pose as smart plug, sending fake power readings to the server interfering with the normal operation.
 \section{Conclusions}

### 2021-03-17 paper/main.tex
push

@@
 \section{System results}
-
+We use Wireshark to monitor our network, while there was intensive traffic over the wireless connection - such as Netflix 1080p streaming (UDP traffic) and a download of Ubuntu operating system ISO (TCP traffic).
+As we know the consistence of miscellaneous traffic type is not very well managed by wireless protocols, our measurements have the scope to guarantee the reliability of our ACK implementation - even only with two smart plugs.
+The packets are sent to the correct client on average within 3.3 ms.
  \section{Consumption}

### 2021-03-18 paper/main.tex
corrections in system results and challenges

--- 2021-03-17 paper/main.tex
@@
 \section{System results}
-
+We used Wireshark to monitor our network while running the system.
+Generally, TCP traffic worsens the performances of UDP in wireless applications.
+Therefore, during the test, we had both TCP and UDP third-party traffic, in particular, we had a 1080p Netflix streaming (UDP) and a download of a Ubuntu ISO (TCP).
+The main objective of the test was to check the efficacy of our version of reliable UDP, so the focus was on the reception of acknowledgments by the server.
+The packets are sent to the correct client on average within 3.3 ms.
  \section{Consumption}
@@
 Since the focus of the project wasn't on security we decided for ease of debugging to do not encrypt the packets exchanged between plugs and server.
-The plugs configuration is hard-coded, for example the Wi-Fi SSID and password are stored as a char array in our C++ code.
+Another issue is that the configuration of the plug is hard-coded, for example, the Wi-Fi SSID and password are stored as a char array in our C++ code.
 Since the EPS 8266 could switch to access point mode which means generate a new wireless network, a configuration procedure could be implemented.
 A device - such as a smartphone - could connect to the plug wireless network and send the SSID and password required by our home wireless settings.
-Those information should be stored in a persistent drive - as a micro SD card - and also, in order to not increase the POC complexity and keep the costs low, we did not implemented those procedures.
-Another challenge to face is the security issue, the information send from a plug to the server are completely clear, so there is no encryption implemented.
-A man-in-the-middle attack could intercept those packages and change their contents.
-An attackers could also pose as smart plug, sending fake power readings to the server interfering with the normal operation.
+That information should be stored in a persistent drive - like a micro SD card.
+Another challenge to face is the security issue, the information sent from a plug to the server is completely clear, so there is no encryption implemented.
+A man-in-the-middle attack could intercept those packets and change their contents.
+An attacker could also pose as a smart plug, sending fake power readings to the server interfering with the normal operation.
+
 \section{Conclusions}

### 2021-03-19 paper/main.tex
new graph
aggiunte robe

@@
 Once the packet has been received, each plug saves the information about the server and is not replying to this type of messages for a certain amount of type, or until a hard reset is performed.
-Then, the plug starts to send \textit{UPDATE messages} to inform the server about energy consumption variation. To do so, a thread keeps watch over the readings provided by the PZEM sensor.
+Then, the plug starts to send \textit{UPDATE messages} to inform the server about energy consumption variation.
+To do so, a thread keeps watch over the readings provided by the PZEM sensor \cite{8442052}\cite{8250475} which integrates an ADC  system  in  one integrated circuit \cite{8612412}.
 The content of the packets is first defined as a JSON object and then serialized to the bytes that are the payload of the UDP packet.
@@
 To do this we used PacketSender to simulate the traffic generated by the plug but not the acknowledgments and Wireshark, a packet analyzer, to check the correct re-transmission of packets by the server by first filtering the traffic by port and type.
+The PZEM power monitor, according to \cite{9264926}, has an error rate based on the device characteristics, so we adopted different margin rates depending on the power consumption assigned to the device type.
 Finally, the entire system has been tested to check the correct transmission of acknowledgments by the plugs.
-
-\section{System results}
-We used Wireshark to monitor our network while running the system.
-Generally, TCP traffic worsens the performances of UDP in wireless applications.
-Therefore, during the test, we had both TCP and UDP third-party traffic, in particular, we had a 1080p Netflix streaming (UDP) and a download of a Ubuntu ISO (TCP).
-The main objective of the test was to check the efficacy of our version of reliable UDP, so the focus was on the reception of acknowledgments by the server.
-The packets are sent to the correct client on average within 3.3 ms.
- \section{Consumption}
-%Qui mettiamo workflow generale con immagine algoritmo
 
@@
 
+\section{System results}
+We used Wireshark to monitor our network while running the system.
+Generally, TCP traffic worsens the performances of UDP in wireless applications.
+Therefore, during the test, we had both TCP and UDP third-party traffic, in particular, we had a 1080p Netflix streaming (UDP) and a download of a Ubuntu ISO (TCP).
+The main objective of the test was to check the efficacy of our version of reliable UDP, so the focus was on the reception of acknowledgments by the server.
+The packets are sent to the correct client on average within 3.3 ms.
+
+\begin{figure}[htbp]
+	\centering
+	\includegraphics[width=\linewidth]{assets/grafico}
+	\caption{Web interface used to control the whole system}
+	\label{fig:grafico}
+\end{figure}
+
 \section{Conclusions}
@@
 
-%
-%\subsection{Maintaining the Integrity of the Specifications}
-%
-%The IEEEtran class file is used to format your paper and style the text. All margins, 
-%column widths, line spaces, and text fonts are prescribed; please do not 
-%alter them. You may note peculiarities. For example, the head margin
-%measures proportionately more than is customary. This measurement 
-%and others are deliberate, using specifications that anticipate your paper 
-%as one part of the entire proceedings, and not as an independent document. 
-%Please do not revise any of the current designations.
-%
-%\section{Prepare Your Paper Before Styling}
-%Before you begin to format your paper, first write and save the content as a 
-%separate text file. Complete all content and organizational editing before 
-%formatting. Please note sections \ref{AA}--\ref{SCM} below for more information on 
-%proofreading, spelling and grammar.
-%
-%Keep your text and graphic files separate until after the text has been 
-%formatted and styled. Do not number text heads---{\LaTeX} will do that 
-%for you.
-%
-%\subsection{Abbreviations and Acronyms}\label{AA}
-%Define abbreviations and acronyms the first time they are used in the text, 
-%even after they have been defined in the abstract. Abbreviations such as 
-%IEEE, SI, MKS, CGS, ac, dc, and rms do not have to be defined. Do not use 
-%abbreviations in the title or heads unless they are unavoidable.
-%
-%\subsection{Units}
-%\begin{itemize}
-%\item Use either SI (MKS) or CGS as primary units.
-(SI units are encouraged.) English units may be used as secondary units (in parentheses).
-An exception would be the use of English units as identifiers in trade, such as ``3.5-inch disk drive''.
-%\item Avoid combining SI and CGS units, such as current in amperes and magnetic field in oersteds.
-This often leads to confusion because equations do not balance dimensionally.
-If you must use mixed units, clearly state the units for each quantity that you use in an equation.
-%\item Do not mix complete spellings and abbreviations of units: ``Wb/m\textsuperscript{2}'' or ``webers per square meter'', not ``webers/m\textsuperscript{2}''.
-Spell out units when they appear in text: ``.
-.
-.
-a few henries'', not ``.
-.
-.
-a few H''.
-%\item Use a zero before decimal points: ``0.25'', not ``.25''. Use ``cm\textsuperscript{3}'', not ``cc''.)
-%\end{itemize}
-%
-%\subsection{Equations}
-%Number equations consecutively. To make your 
-%equations more compact, you may use the solidus (~/~), the exp function, or 
-%appropriate exponents. Italicize Roman symbols for quantities and variables, 
-%but not Greek symbols. Use a long dash rather than a hyphen for a minus 
-%sign. Punctuate equations with commas or periods when they are part of a 
-%sentence, as in:
-%\begin{equation}
-%a+b=\gamma\label{eq}
-%\end{equation}
-%
-%Be sure that the 
-%symbols in your equation have been defined before or immediately following 
-%the equation. Use ``\eqref{eq}'', not ``Eq.~\eqref{eq}'' or ``equation \eqref{eq}'', except at 
-%the beginning of a sentence: ``Equation \eqref{eq} is . . .''
-%
-%\subsection{\LaTeX-Specific Advice}
-%
-%Please use ``soft'' (e.g., \verb|\eqref{Eq}|) cross references instead
-%of ``hard'' references (e.g., \verb|(1)|). That will make it possible
-%to combine sections, add equations, or change the order of figures or
-%citations without having to go through the file line by line.
-%
-%Please don't use the \verb|{eqnarray}| equation environment. Use
-%\verb|{align}| or \verb|{IEEEeqnarray}| instead. The \verb|{eqnarray}|
-%environment leaves unsightly spaces around relation symbols.
-%
-%Please note that the \verb|{subequations}| environment in {\LaTeX}
-%will increment the main equation counter even when there are no
-%equation numbers displayed. If you forget that, you might write an
-%article in which the equation numbers skip from (17) to (20), causing
-%the copy editors to wonder if you've discovered a new method of
-%counting.
-%
-%{\BibTeX} does not work by magic. It doesn't get the bibliographic
-%data from thin air but from .bib files. If you use {\BibTeX} to produce a
-%bibliography you must send the .bib files. 
-%
-%{\LaTeX} can't read your mind. If you assign the same label to a
-%subsubsection and a table, you might find that Table I has been cross
-%referenced as Table IV-B3. 
-%
-%{\LaTeX} does not have precognitive abilities. If you put a
-%\verb|\label| command before the command that updates the counter it's
-%supposed to be using, the label will pick up the last counter to be
-%cross referenced instead. In particular, a \verb|\label| command
-%should not go before the caption of a figure or a table.
-%
-%Do not use \verb|\nonumber| inside the \verb|{array}| environment. It
-%will not stop equation numbers inside \verb|{array}| (there won't be
-%any anyway) and it might stop a wanted equation number in the
-%surrounding equation.
-%
-%\subsection{Some Common Mistakes}\label{SCM}
-%\begin{itemize}
-%\item The word ``data'' is plural, not singular.
-%\item The subscript for the permeability of vacuum $\mu_{0}$, and other common scientific constants, is zero with subscript formatting, not a lowercase letter ``o''.
-%\item In American English, commas, semicolons, periods, question and exclamation marks are located within quotation marks only when a complete thought or name is cited, such as a title or full quotation.
-When quotation marks are used, instead of a bold or italic typeface, to highlight a word or phrase, punctuation should appear outside of the quotation marks.
-A parenthetical phrase or statement at the end of a sentence is punctuated outside of the closing parenthesis (like this).
-(A parenthetical sentence is punctuated within the parentheses.)
-%\item A graph within a graph is an ``inset'', not an ``insert''. The word alternatively is preferred to the word ``alternately'' (unless you really mean something that alternates).
-%\item Do not use the word ``essentially'' to mean ``approximately'' or ``effectively''.
-%\item In your paper title, if the words ``that uses'' can accurately replace the word ``using'', capitalize the ``u''; if not, keep using lower-cased.
-%\item Be aware of the different meanings of the homophones ``affect'' and ``effect'', ``complement'' and ``compliment'', ``discreet'' and ``discrete'', ``principal'' and ``principle''.
-%\item Do not confuse ``imply'' and ``infer''.
-%\item The prefix ``non'' is not a word; it should be joined to the word it modifies, usually without a hyphen.
-%\item There is no period after the ``et'' in the Latin abbreviation ``et al.''.
-%\item The abbreviation ``i.e.'' means ``that is'', and the abbreviation ``e.g.'' means ``for example''.
-%\end{itemize}
-%An excellent style manual for science writers is \cite{b7}.
-%
-%\subsection{Authors and Affiliations}
-%\textbf{The class file is designed for, but not limited to, six authors.} A 
-%minimum of one author is required for all conference articles. Author names 
-%should be listed starting from left to right and then moving down to the 
-%next line. This is the author sequence that will be used in future citations 
-%and by indexing services. Names should not be listed in columns nor group by 
-%affiliation. Please keep your affiliations as succinct as possible (for 
-%example, do not differentiate among departments of the same organization).
-%
-%\subsection{Identify the Headings}
-%Headings, or heads, are organizational devices that guide the reader through 
-%your paper. There are two types: component heads and text heads.
-%
-%Component heads identify the different components of your paper and are not 
-%topically subordinate to each other. Examples include Acknowledgments and 
-%References and, for these, the correct style to use is ``Heading 5''. Use 
-%``figure caption'' for your Figure captions, and ``table head'' for your 
-%table title. Run-in heads, such as ``Abstract'', will require you to apply a 
-%style (in this case, italic) in addition to the style provided by the drop 
-%down menu to differentiate the head from the text.
-%
-%Text heads organize the topics on a relational, hierarchical basis. For 
-%example, the paper title is the primary text head because all subsequent 
-%material relates and elaborates on this one topic. If there are two or more 
-%sub-topics, the next level head (uppercase Roman numerals) should be used 
-%and, conversely, if there are not at least two sub-topics, then no subheads 
-%should be introduced.
-%
-%\subsection{Figures and Tables}
-%\paragraph{Positioning Figures and Tables} Place figures and tables at the top and 
-%bottom of columns. Avoid placing them in the middle of columns. Large 
-%figures and tables may span across both columns. Figure captions should be 
-%below the figures; table heads should appear above the tables. Insert 
-%figures and tables after they are cited in the text. Use the abbreviation 
-%``Fig.~\ref{fig}'', even at the beginning of a sentence.
-%
-%\begin{table}[htbp]
-%\caption{Table Type Styles}
-%\begin{center}
-%\begin{tabular}{|c|c|c|c|}
-%\hline
-%\textbf{Table}&\multicolumn{3}{|c|}{\textbf{Table Column Head}} \\
-%\cline{2-4} 
-%\textbf{Head} & \textbf{\textit{Table column subhead}}& \textbf{\textit{Subhead}}& \textbf{\textit{Subhead}} \\
-%\hline
-%copy& More table copy$^{\mathrm{a}}$& &  \\
-%\hline
-%\multicolumn{4}{l}{$^{\mathrm{a}}$Sample of a Table footnote.}
-%\end{tabular}
-%\label{tab1}
-%\end{center}
-%\end{table}
-%
-%\begin{figure}[htbp]
-%\centerline{\includegraphics{fig1.png}}
-%\caption{Example of a figure caption.}
-%\label{fig}
-%\end{figure}
-%
-%Figure Labels: Use 8 point Times New Roman for Figure labels. Use words 
-%rather than symbols or abbreviations when writing Figure axis labels to 
-%avoid confusing the reader. As an example, write the quantity 
-%``Magnetization'', or ``Magnetization, M'', not just ``M''. If including 
-%units in the label, present them within parentheses. Do not label axes only 
-%with units. In the example, write ``Magnetization (A/m)'' or ``Magnetization 
-%\{A[m(1)]\}'', not just ``A/m''. Do not label axes with a ratio of 
-%quantities and units. For example, write ``Temperature (K)'', not 
-%``Temperature/K''.
-%
-%\section*{Acknowledgment}
-%
-%The preferred spelling of the word ``acknowledgment'' in America is without 
-%an ``e'' after the ``g''. Avoid the stilted expression ``one of us (R. B. 
-%G.) thanks $\ldots$''. Instead, try ``R. B. G. thanks$\ldots$''. Put sponsor 
-%acknowledgments in the unnumbered footnote on the first page.
-
 \bibliography{references.bib}{}

### 2021-03-19 paper/main.tex
grammarly, 2 citations

@@
 The smart plug is a small power plug which consists of a WeMos D1 R2 board, a 220v relay that can be controlled using 5 volts digital signals, and a coil connected to a PZEM-004T sensor which provides the readings to WeMos through its digital pins.
+The hardware has been chosen to be low-cost and accurate \cite{8442066}.
 The connection scheme is represented in Figure~\ref{fig:pcbschema}, and has a cost about €15, so it is not that expensive. 
@@
 Finally, the \verb|ACK| packet has the \verb|sts| field too, and has a field \verb|timestamp| which value is taken from the same field in the packet the plug received from the server.
-In order to switch correctly the relay, the board waits for \textit{ON/OFF messages} from the server.
+To switch correctly the relay, the board waits for \textit{ON/OFF messages} from the server.
 After those requests have been received correctly, the correct action is performed and then an \textit{ACK message} is sent to inform the server about the successful receipt of the command.
@@
 The GUI shown in Figure~\ref{fig:simulatedwebapp} presents a switch where the user can turn on or off the plug.
-If there is not enough energy available to turn on a device, the switch will be displayed as disabled in order to avoid a blackout.
+If there is not enough energy available to turn on a device, the switch will be displayed as disabled to avoid a blackout.
 \begin{figure}[htbp]
@@
 \section{Methods}
-Throughout the development, the communication between the server and the plug has been simulated and tested using PacketSender.
+Throughout the development, the communication between the server and the plug has been simulated and tested using PacketSender \cite{packetsender}.
 This tool allows the user to define the content of a packet in ASCII format, this is turned into bytes and sent to the specified address and port.

### 2021-03-21 paper/main.tex
correzioni

@@
 In our POC, we have modified the architecture described in \cite{8110428} obtaining a specific low-energy consumption-driven infrastructure.
-This consists of the smart plugs, a computer (for the server), and a device (for the web interface).
+This consists of the smart plugs, a computer or a Raspberry Pi running  the server, and the control devices which interact with the system through the web interface.
 In a home scenario, these devices are connected to the home wireless router.
 The communication between smart plugs and server occurs over UDP with a simple form of reliability implemented at the application level and tested using Wireshark \cite{wireshark}.
-The architecture implemented differs from the most common ones in two major aspects: first, most homes aren't equipped with this kind of system, instead, a circuit breaker triggers for safety reasons when too much power is being consumed.
-Second, when a similar system is used it usually relies on cloud computing or external services.
+The architecture implemented differs from the most common ones in two major aspects: first, most homes aren't equipped with this kind of system, instead, a circuit breaker is triggered when too much power is being consumed.
+Second, when a similar system is used, it usually relies on cloud computing or external services.
 In contrast, our system offers the functionalities already described and both computing and data storage are performed locally.
@@
 The architecture of the system is such that if need be it can be easily modified to use third-party services.
-The smart plugs have been prototyped using Arduino and the server has been written in Java.
-Let's now consider a use case example: the user sets the maximum power consumption possible in the home and then turns on two appliances.
+For example, consider the following use case: the user sets the maximum power consumption possible in the home and then turns on two appliances.
 When this happens for the first time the system decides, based on the type of appliance connected, a default value for the maximum power usage of the appliance.
@@
 Our POC covers this use case and shows that such a system can be practical and useful and that the traffic generated isn't enough to sensibly worsen the performances of the typical home WLAN.
-To summarize, the system keeps the power usage from reaching the maximum limit set by the user by forbidding the power-on of appliances that consume more than the available power.
+To summarize, the system keeps the power usage from reaching the maximum limit set by the user by forbidding the power-on of appliances that consume more than the available power avoiding blackouts.
 It also gives granular information about the energy consumption of the device and allows the user to turn on or off appliances remotely (via web interface).
-Aside from the main use case, in the age of climate awareness, such a system could be interesting to an environmentally conscious user that can monitor the power usage of appliances but also could set the maximum power consumption to be lower than the real one to use less power or save money.
+Aside from the main use case, in the age of climate awareness, such a system could be interesting to an environmentally conscious user that can monitor the power usage of appliances but also could set the maximum power consumption to be lower than the real one to use less power and save money.
 
@@
 The general architecture has three main components: the smart plugs, the server, and the web interface.
-The smart plugs have been prototyped using Arduino.
+The smart plugs have been prototyped using Arduino IDE.
 The server has been developed in Java and the web interface is written in React.
-The rundown of what each part does is as follows: Arduino drives a sensor that gathers data on the power consumption of the plug and communicates with the UDP server that keeps track of the plugs and their energy consumption.
+The rundown of what each part does is made up of a WeMos D1 R2, an Arduino-like board, monitors a sensor that gathers data on the power consumption and controls a relay which turns on or off the plug.
+It communicates over wireless with the UDP server that keeps track of the plugs and their energy consumption.
 The web interface uses an API exposed by the server to let the user see and control the status of each plug.
@@
 \subsection{Smart plugs}\label{SP}
-The smart plug is a small power plug which consists of a WeMos D1 R2 board, a 220v relay that can be controlled using 5 volts digital signals, and a coil connected to a PZEM-004T sensor which provides the readings to WeMos through its digital pins.
+The smart plug is a small power plug which consists of a WeMos D1 R2 board, a 220v relay that can be controlled using 5 volts digital signals, and a coil connected to a PZEM-004T sensor \cite{8442052} \cite{8250475}  which provides the readings to WeMos through its digital pins.
 The hardware has been chosen to be low-cost and accurate \cite{8442066}.
@@
 Then, the plug starts to send \textit{UPDATE messages} to inform the server about energy consumption variation.
-To do so, a thread keeps watch over the readings provided by the PZEM sensor \cite{8442052}\cite{8250475} which integrates an ADC  system  in  one integrated circuit \cite{8612412}.
+To do so, a thread keeps watch over the readings provided by the PZEM sensor which integrates an ADC  system  in  one integrated circuit \cite{8612412}.
 The content of the packets is first defined as a JSON object and then serialized to the bytes that are the payload of the UDP packet.
@@
 \end{itemize}
-The \verb|UPDATE| packet has a \verb|type| field too, and has a field \verb|active_power| that is a reading of the currently consumed watts.
-Finally, the \verb|ACK| packet has the \verb|sts| field too, and has a field \verb|timestamp| which value is taken from the same field in the packet the plug received from the server.
+The \verb|UPDATE| packet has a \verb|type| and \verb|active_power| fields.
+This latter is the last watt usage read at time $t$.
+Finally, the \verb|ACK| packet has the \verb|timestamp| filed, which value is taken from the same field in the packet the plug received from the server as unique identifier for that packet.
 To switch correctly the relay, the board waits for \textit{ON/OFF messages} from the server.
@@
 	\centering
-	\includegraphics[width=0.7\linewidth]{assets/IMG_5348}
+	\includegraphics[width=\linewidth]{assets/IMG_5348}
 	\caption{Proof of concept of our smart plug}
@@
 Tomcat is implemented to expose the servlet API.
-The server has the following responsibilities: to periodically broadcasts \textit{INIT packets} to let the plugs know its address; It listens for connections and updates from the plugs; it waits for acknowledgments from the plugs and, in case they are not received, it retransmits the lost packets; it exposes servlets to let the web interface get information about the plugs and send \textit{ON/OFF packets}.
-The periodic actions, namely, sending the \textit{INIT packet} and retransmitting those that are lost, are implemented as extensions of \textit{Guava's AbstractScheduledService} which allows performing of these at constant intervals.
-Another thread waits and manages the plugs' responses.
+The server periodically broadcasts \textit{INIT packets} to let the plugs know its address and it listens for connections and updates from the plugs.
+Furthermore, it waits for acknowledgments from the plugs and, in case they are not received, and it re-transmits the lost packets and exposes servlets to let the web interface get information, about the plugs and send \textit{ON/OFF packets}.
+The periodic actions, namely, sending the \textit{INIT packet} and re-transmitting those that are lost, are implemented as extensions of \textit{Guava's AbstractScheduledService} which allows performing of these at constant intervals.
+Another thread waits and manages the plugs replies.
 When a plug responds to the \textit{INIT packet} the server will register its information and estimate the max power consumption for the appliance connected to the plug.
@@
 When a plug sends an \textit{UPDATE packet} the server will update its registered information, most important: the current energy consumption and the max energy consumption.
-Finally, the server waits for the acknowledgments of previously sent packets.
-These packets contain a timestamp which is sent back by the plugs in the acknowledgments.
-The server also has a list of packets waiting for acknowledgment, in this way when the server receives an ACK it can discard the packet with the given timestamp.
+Finally, the server waits for the acknowledgments of previously ON or OFF packets.
+These packets contain a \verb|timestamp| field which is sent back by the plugs in the acknowledgments.
+The server has a list of packets waiting for acknowledgment, in this way when the server receives an ACK it can discard the packet with the given timestamp.
 If a configurable number of seconds elapses before this happens the packet will be sent again.
@@
 \end{itemize}
-\verb|ON| and \verb|OFF| packets also have a field \verb|timestamp| which contains a string representation of the timestamp.  
 \begin{figure}
@@
 \end{figure}
-The servlets simply allow the web interface to get the server's information about the plugs (the type of appliance connected, the current energy consumption, and more) and to turn on or off any given plug.
+The servlets simply allow the web interface to get the server information about the plugs (the type of appliance connected, the current energy consumption, and more) and to turn on or off any given plug.
 In this last case, a packet will be sent by the server and for it the server will wait an acknowledgment.
@@
 Generally, TCP traffic worsens the performances of UDP in wireless applications.
-Therefore, during the test, we had both TCP and UDP third-party traffic, in particular, we had a 1080p Netflix streaming (UDP) and a download of a Ubuntu ISO (TCP).
+Therefore, during the test, we had both TCP and UDP third-party traffic, in particular, we had a Apex Legends game  (UDP) and a normal web navigation (TCP).
 The main objective of the test was to check the efficacy of our version of reliable UDP, so the focus was on the reception of acknowledgments by the server.
-The packets are sent to the correct client on average within 3.3 ms.
+The packets are sent to the correct client, even in a scenario with different traffic types.
 

### 2021-03-21 paper/main.tex
grammarly

@@
 The server has been developed in Java and the web interface is written in React.
-The rundown of what each part does is made up of a WeMos D1 R2, an Arduino-like board, monitors a sensor that gathers data on the power consumption and controls a relay which turns on or off the plug.
+The rundown of what each part does is made up of a WeMos D1 R2, an Arduino-like board, monitors a sensor that gathers data on the power consumption, and controls a relay that turns on or off the plug.
 It communicates over wireless with the UDP server that keeps track of the plugs and their energy consumption.
@@
 	\subsection{Smart plugs}\label{SP}
-The smart plug is a small power plug which consists of a WeMos D1 R2 board, a 220v relay that can be controlled using 5 volts digital signals, and a coil connected to a PZEM-004T sensor \cite{8442052} \cite{8250475}  which provides the readings to WeMos through its digital pins.
+	The smart plug is a small power plug that consists of a WeMos D1 R2 board, a 220v relay that can be controlled using 5 volts digital signals, and a coil connected to a PZEM-004T sensor \cite{8442052} \cite{8250475}  which provides the readings to WeMos through its digital pins.
 The hardware has been chosen to be low-cost and accurate \cite{8442066}.
-The connection scheme is represented in Figure~\ref{fig:pcbschema}, and has a cost about €15, so it is not that expensive. 
+	The connection scheme is represented in Figure~\ref{fig:pcbschema}, and has a cost of about €15, so it is not that expensive. 
 	The WeMos D1 R2 board is equipped with a EPS 8266 wireless module operating at 2.4GHz.
@@
 	First, smart plugs wait for an \textit{INIT message}, sent by the server via broadcast.
-Once the packet has been received, each plug saves the information about the server and is not replying to this type of messages for a certain amount of type, or until a hard reset is performed.
+Once the packet has been received, each plug saves the information about the server and is not replying to this type of message for a certain amount of type, or until a hard reset is performed.
 	Then, the plug starts to send \textit{UPDATE messages} to inform the server about energy consumption variation.
@@
 This latter is the last watt usage read at time $t$.
-Finally, the \verb|ACK| packet has the \verb|timestamp| filed, which value is taken from the same field in the packet the plug received from the server as unique identifier for that packet.
+Finally, the \verb|ACK| packet has the \verb|timestamp| filed, which value is taken from the same field in the packet the plug received from the server as a unique identifier for that packet.
 	To switch correctly the relay, the board waits for \textit{ON/OFF messages} from the server.
@@
 The server periodically broadcasts \textit{INIT packets} to let the plugs know its address and it listens for connections and updates from the plugs.
-Furthermore, it waits for acknowledgments from the plugs and, in case they are not received, and it re-transmits the lost packets and exposes servlets to let the web interface get information, about the plugs and send \textit{ON/OFF packets}.
+Furthermore, it waits for acknowledgments from the plugs and, in case they are not received, and re-transmits the lost packets and exposes servlets to let the web interface get information, about the plugs and send \textit{ON/OFF packets}.
 The periodic actions, namely, sending the \textit{INIT packet} and re-transmitting those that are lost, are implemented as extensions of \textit{Guava's AbstractScheduledService} which allows performing of these at constant intervals.
@@
 	The servlets simply allow the web interface to get the server information about the plugs (the type of appliance connected, the current energy consumption, and more) and to turn on or off any given plug.
-In this last case, a packet will be sent by the server and for it the server will wait an acknowledgment.
+In this last case, a packet will be sent by the server and for it, the server will wait for an acknowledgment.
 The information about the plugs saved by the server is kept as a \textit{thread-safe hashmap}.
-Some of this information, such as the IP address of the plugs, the type of appliance connected and the max power consumption is also saved in a \textit{XML file} to avoid loosing it in case of a server malfunction or restart.
+Some of this information, such as the IP address of the plugs, the type of appliance connected, and the max power consumption is also saved in a \textit{XML file} to avoid losing it in case of a server malfunction or restart.
 
@@
 	The web interface is written in React using Bootstrap and exposes a way to interact with the server to get the real-time power consumption for each plug and managing the connected devices.
-The polling calls to the API exposed by the server through the servlets are performed over HTTP and thefore using the TCP protocol.
+The polling calls to the API exposed by the server through the servlets are performed over HTTP and therefore using the TCP protocol.
 The GUI shown in Figure~\ref{fig:simulatedwebapp} presents a switch where the user can turn on or off the plug.
@@
 Generally, TCP traffic worsens the performances of UDP in wireless applications.
-Therefore, during the test, we had both TCP and UDP third-party traffic, in particular, we had a Apex Legends game  (UDP) and a normal web navigation (TCP).
+Therefore, during the test, we had both TCP and UDP third-party traffic, in particular, we had an Apex Legends game (UDP) and normal web navigation (TCP).
 The main objective of the test was to check the efficacy of our version of reliable UDP, so the focus was on the reception of acknowledgments by the server.

### 2021-03-21 paper/main.tex
sistemato

@@
 This consists of the smart plugs, a computer or a Raspberry Pi running the server, and the control devices which interact with the system through the web interface.
-In a home scenario, these devices are connected to the home wireless router.
+In a household scenario, these devices are connected to the home wireless router.
 The communication between smart plugs and server occurs over UDP with a simple form of reliability implemented at the application level and tested using Wireshark \cite{wireshark}.
-The architecture implemented differs from the most common ones in two major aspects: first, most homes aren't equipped with this kind of system, instead, a circuit breaker is triggered when too much power is being consumed.
+The architecture implemented differs from the most common ones in two major aspects: first, most houses aren't equipped with this kind of system, instead, a circuit breaker is triggered when too much power is being consumed.
 Second, when a similar system is used, it usually relies on cloud computing or external services.
@@
 It also gives granular information about the energy consumption of the device and allows the user to turn on or off appliances remotely (via web interface).
-Aside from the main use case, in the age of climate awareness, such a system could be interesting to an environmentally conscious user that can monitor the power usage of appliances but also could set the maximum power consumption to be lower than the real one to use less power and save money.
+Aside from the main use case, in the age of climate awareness, such a system could be interesting to an environmentally conscious user that can monitor the power usage of appliances, but also could set the maximum power consumption to be lower than the real one to use less power and save money.
 
@@
 	The general architecture has three main components: the smart plugs, the server, and the web interface.
-The smart plugs have been prototyped using Arduino IDE.
-The server has been developed in Java and the web interface is written in React.
-The rundown of what each part does is made up of a WeMos D1 R2, an Arduino-like board, monitors a sensor that gathers data on the power consumption, and controls a relay that turns on or off the plug.
+The smart plugs code have been written using Arduino IDE in C++.
+Instead, the server has been developed in Java and the web interface is written in React.
+The rundown of what each part does is made up of a WeMos D1 R2, an Arduino-like board, monitors a sensor that gathers data on the power consumption, and controls a relay that turns on or off the appliance.
 It communicates over wireless with the UDP server that keeps track of the plugs and their energy consumption.
@@
 	\subsection{Smart plugs}\label{SP}
-	The smart plug is a small power plug that consists of a WeMos D1 R2 board, a 220v relay that can be controlled using 5 volts digital signals, and a coil connected to a PZEM-004T sensor \cite{8442052} \cite{8250475}  which provides the readings to WeMos through its digital pins.
+	The smart plug is a small power plug that consists of a WeMos D1 R2 board, a 220v relay that can be controlled using digital signals, and a coil connected to a PZEM-004T sensor \cite{8442052} \cite{8250475}  which provides the readings to WeMos through its digital pins.
 The hardware has been chosen to be low-cost and accurate \cite{8442066}.
@@
 	\begin{itemize}
-		\item \begin{spverbatim}"INIT"\end{spverbatim} when responding to the server's INIT packet;
+		\item \begin{spverbatim}"INIT"\end{spverbatim} when responding to the server INIT packet;
 		\item \begin{spverbatim}"UPDATE"\end{spverbatim} when sending an update to the server;
@@
 This latter is the last watt usage read at time $t$.
-Finally, the \verb|ACK| packet has the \verb|timestamp| filed, which value is taken from the same field in the packet the plug received from the server as a unique identifier for that packet.
+Finally, the \verb|ACK| packet has the \verb|timestamp| filed, which value is taken from the same field in the plug UDP packet received from the server as a unique identifier for that packet.
 	To switch correctly the relay, the board waits for \textit{ON/OFF messages} from the server.
@@
 The server periodically broadcasts \textit{INIT packets} to let the plugs know its address and it listens for connections and updates from the plugs.
-Furthermore, it waits for acknowledgments from the plugs and, in case they are not received, and re-transmits the lost packets and exposes servlets to let the web interface get information, about the plugs and send \textit{ON/OFF packets}.
+Furthermore, it waits for acknowledgments and, in case they are not received re-transmits the lost packets.
+Finally, it exposes servlets to let the web interface get information, about the plugs and send \textit{ON/OFF packets}.
 The periodic actions, namely, sending the \textit{INIT packet} and re-transmitting those that are lost, are implemented as extensions of \textit{Guava's AbstractScheduledService} which allows performing of these at constant intervals.
 Another thread waits and manages the plugs replies.
-When a plug responds to the \textit{INIT packet} the server will register its information and estimate the max power consumption for the appliance connected to the plug.
+When a plug responds to the \textit{INIT packet}, the server will register its information and estimate the max power consumption for the appliance connected to the plug.
 This value is simply based on average values for the given appliance type as found on Google.
@@
 	The servlets simply allow the web interface to get the server information about the plugs (the type of appliance connected, the current energy consumption, and more) and to turn on or off any given plug.
-In this last case, a packet will be sent by the server and for it, the server will wait for an acknowledgment.
+In this last case, a packet will be sent by the server and for it, and this latter will wait for an acknowledgment.
 The information about the plugs saved by the server is kept as a \textit{thread-safe hashmap}.
@@
 That information should be stored in a persistent drive - like a micro SD card.
-	Another challenge to face is the security issue, the information sent from a plug to the server is completely clear, so there is no encryption implemented.
+	As we already mentioned, another challenge to face is the security issue, the information sent from a plug to the server is completely clear, so there is no encryption implemented.
 A man-in-the-middle attack could intercept those packets and change their contents.
@@
 Generally, TCP traffic worsens the performances of UDP in wireless applications.
-Therefore, during the test, we had both TCP and UDP third-party traffic, in particular, we had an Apex Legends game (UDP) and normal web navigation (TCP).
+In particular, during the test, we had both TCP and UDP third-party traffic, in particular, we had an Apex Legends game (UDP) and normal web navigation (TCP).
 The main objective of the test was to check the efficacy of our version of reliable UDP, so the focus was on the reception of acknowledgments by the server.
@@
 		\includegraphics[width=\linewidth]{assets/grafico}
-		\caption{Web interface used to control the whole system}
+		\caption{Network traffic analysis chart. The green line is the UDP  traffic generated by our system implementation, and it impacts on the whole network traffic}
 		\label{fig:grafico}
@@
 These plugs can reliably operate using the UDP protocol provided there are some reliability checks at the application level and can do it in a busy home WLAN where traffic can be both TCP and UDP.
-
+	Our POC provides an idea of wireless plugs which avoids the home blackouts, and in the meantime helps our planet making people more conscientious about wasting energy.
 	\bibliography{references.bib}{}

### 2021-03-26 paper/main.tex
new stuff

@@
 The communication between smart plugs and server occurs over UDP with a simple form of reliability implemented at the application level and tested using Wireshark \cite{wireshark}.
-The architecture implemented differs from the most common ones in two major aspects: first, most houses aren't equipped with this kind of system, instead, a circuit breaker is triggered when too much power is being consumed.
+The architecture implemented differs from the most common ones in two major aspects: first, most houses are not equipped with this kind of system, instead, a circuit breaker is triggered when too much power is being consumed.
 Second, when a similar system is used, it usually relies on cloud computing or external services.
@@
 This can be an advantage in terms of both privacy and security.
-Furthermore, this is an advantage in terms of reliability: our system doesn't need an internet connection to work properly, instead, it just needs a working WLAN.
-However, while this aspect is significant, the development of the prototype hasn't focused on the security aspects and some issues will be discussed in the appropriate section.
+Furthermore, this is an advantage in terms of reliability: our system does not need an Internet connection to work properly, instead, it just needs a working WLAN.
+However, while this aspect is significant, the development of the prototype has not focused on the security aspects and some issues will be discussed in the appropriate section.
 The architecture of the system is such that if need be it can be easily modified to use third-party services.
@@
 Now that the system is running and some appliances are turned on, the user will be able to switch on only the appliances that consume less than the available power.
-Our POC covers this use case and shows that such a system can be practical and useful and that the traffic generated isn't enough to sensibly worsen the performances of the typical home WLAN.
+Our POC covers this use case and shows that such a system can be practical and useful and that the traffic generated is not enough to sensibly worsen the performances of the typical home WLAN.
 To summarize, the system keeps the power usage from reaching the maximum limit set by the user by forbidding the power-on of appliances that consume more than the available power avoiding blackouts.
@@
 The hardware has been chosen to be low-cost and accurate \cite{8442066}.
-	The connection scheme is represented in Figure~\ref{fig:pcbschema}, and has a cost of about €15, so it is not that expensive. 
+	The connection scheme is represented in Figure~\ref{fig:pcbschema}, and has a cost of about €15, so it is not that expensive. The smart plug can be seen in Figure~\ref{fig:img5348}.
 	The WeMos D1 R2 board is equipped with a EPS 8266 wireless module operating at 2.4GHz.
@@
 	First, smart plugs wait for an \textit{INIT message}, sent by the server via broadcast.
-Once the packet has been received, each plug saves the information about the server and is not replying to this type of message for a certain amount of type, or until a hard reset is performed.
+Once the packet has been received, each plug saves the information about the server and is not replying to this type of message for a certain amount of time, or until a hard reset is performed.
 	Then, the plug starts to send \textit{UPDATE messages} to inform the server about energy consumption variation.
 To do so, a thread keeps watch over the readings provided by the PZEM sensor which integrates an ADC  system  in one integrated circuit \cite{8612412}.
+	A summary of the interactions between plug and server is given in Figure~\ref{fig:plugserverinteraction}.
 	The content of the packets is first defined as a JSON object and then serialized to the bytes that are the payload of the UDP packet.
@@
 	\end{figure}
+	\begin{figure}[htbp]
+		\centering
+		\includegraphics[width=0.7\linewidth]{assets/plugserverinteraction}
+		\caption{Interaction between smart plugs and server}
+		\label{fig:plugserverinteraction}
+	\end{figure}
 
@@
 Finally, the server waits for the acknowledgments of previously ON or OFF packets.
-These packets contain a \verb|timestamp| field which is sent back by the plugs in the acknowledgments.
+A summary of the logic used by the server is shown in Figure~\ref{fig:server_logic}.
+ON/OFF packets contain a \verb|timestamp| field which is sent back by the plugs in the acknowledgments.
 The server has a list of packets waiting for acknowledgment, in this way when the server receives an ACK it can discard the packet with the given timestamp.
@@
 	During the development, we found some issues outside the scope of this POC.
-Since the focus of the project wasn't on security we decided for ease of debugging to do not encrypt the packets exchanged between plugs and server.
+Since the focus of the project was not on security we decided for ease of debugging to do not encrypt the packets exchanged between plugs and server.
 Another issue is that the configuration of the plug is hard-coded, for example, the Wi-Fi SSID and password are stored as a char array in our C++ code.
@@
 An attacker could also pose as a smart plug, sending fake power readings to the server interfering with the normal operation.
+	\subsection{Security}
 
@@
 The packets are sent to the correct client, even in a scenario with different traffic types.
+The traffic generated by the system is not much as can be seen in Figure~\ref{fig:grafico}.
+
+	\section{Related Works}
+	With respect to other state of the art smart plug systems such as \cite{8612412}, \cite{8110428}, our approach uses UDP instead of TCP.
+The theoretical advantage of using UDP is that we avoid the TCP overhead that is not needed in this kind of application, however, since the traffic generated is so little, empirical evidence of this advantage may only be manifest within a system with a large number of smart plugs connected.
 

### 2021-03-26 paper/main.tex
fdgbfdg

@@
 Aside from the main use case, in the age of climate awareness, such a system could be interesting to an environmentally conscious user that can monitor the power usage of appliances, but also could set the maximum power consumption to be lower than the real one to use less power and save money.
-
+		\section{State of the Art}
+	Smart plugs with power consumption detection are commonly used in the same household scenarios, but they implement different workflows and protocols.
+In fact, usually to realize these IoT devices an external platform is integrated with the main board (Arduino, Raspberry Pi, generic boards with EPS 8266) .
+In most cases, this platform is Blynk, which is a hardware-agnostic IoT platform and allows to configure our board in many different ways.
+	The user could use the cloud infrastructure provided by the Blynk company, or, since the source code is open-source, download and install their own server. 
+	This latter scenario is the preferred one since is free, and consist of the Blink server, the blink app and the smart devices, which uses Blynk API to perform the connections.
+A Blynk installation is generic-purpose, so you could install and control different types of devices and show the measurements using only the TCP protocols.
+Anyway, app user interface needs to be customized and the server needs a database, so the configuration requires much time.
+Instead, our system - as described in the following paragraphs - has a different goal and provides essential features to manage the smart plugs.
+The aim of our project is to create a functional IoT system which avoids blackouts and in the meantime has a low impact on the wireless network using a modified version of the UDP protocol.
+	Although, Blynk implements some security feature which makes it more secure respect to our system.  
 	\section{General architecture}

### 2021-03-26 paper/main.tex
related work

@@
 Aside from the main use case, in the age of climate awareness, such a system could be interesting to an environmentally conscious user that can monitor the power usage of appliances, but also could set the maximum power consumption to be lower than the real one to use less power and save money.
+
+	\section{Related Work}
+	Different designs have been proposed for this kind of application.
+In \cite{7884488} a wireless sensor network is implemented using ZigBee.
+In \cite{8612412}, \cite{8110428} the communication protocol used is TCP over WiFi.
+In our work we use UDP over the home WLAN.
+The theoretical advantage of using UDP is that we avoid the TCP overhead that is not needed in this kind of application, however, since the traffic generated is so little, empirical evidence of this advantage may only be manifest within a system with a large number of smart plugs connected.
+Differently from other  proposed works, on top of the energy monitoring system, we implement a mechanism that keeps the user from exceeding a configurable maximum power usage.
+
 	\section{State of the Art}
@@
 	Although, Blynk implements some security feature which makes it more secure respect to our system.
+
 	\section{General architecture}
@@
 
-	\section{Related Works}
-	With respect to other state of the art smart plug systems such as \cite{8612412}, \cite{8110428}, our approach uses UDP instead of TCP.
-The theoretical advantage of using UDP is that we avoid the TCP overhead that is not needed in this kind of application, however, since the traffic generated is so little, empirical evidence of this advantage may only be manifest within a system with a large number of smart plugs connected.
-
 	\begin{figure}[htbp]

### 2021-03-26 paper/main.tex
sicurezza

@@
 	Different designs have been proposed for this kind of application.
-In \cite{7884488} a wireless sensor network is implemented using ZigBee.
-In \cite{8612412}, \cite{8110428} the communication protocol used is TCP over WiFi.
-In our work we use UDP over the home WLAN.
+In \cite{7884488} a wireless sensor network is implemented using ZigBee, which is more indicated for IoT scenarios.
+In \cite{8612412}, \cite{8110428} the communication protocol used is TCP over wireless.
+In our POC, we use UDP over a wireless connection.
 The theoretical advantage of using UDP is that we avoid the TCP overhead that is not needed in this kind of application, however, since the traffic generated is so little, empirical evidence of this advantage may only be manifest within a system with a large number of smart plugs connected.
@@
 That information should be stored in a persistent drive - like a micro SD card.
+	\section{Security issues}
 	As we already mentioned, another challenge to face is the security issue, the information sent from a plug to the server is completely clear, so there is no encryption implemented. 
-A man-in-the-middle attack could intercept those packets and change their contents.
-An attacker could also pose as a smart plug, sending fake power readings to the server interfering with the normal operation.
-	\subsection{Security}
+	In fact, our aim is to create a smart system and for debugging purpose is more convenient to use un-encrypted packets.
+	 The following paragraphs describes different attacks which we have implemented or could be performed quite easily.
+	\subsection{Fake plugs}
+	A fake plug could be easily added to our system sending fake readings. In our scenario this could be a problem, because could lead to a different behavior.
+	If an attacker uses a fake plug could send a random value to the system avoiding the user to turn on the correct device, considering that the system sums the energy consumption to prevent blackouts.
+An identification mechanism, for example using a token validation procedure, could be implemented to recognize and guarantee the access to authorized devices.
+An example of fake plug is the NodeMcu V3, which is used for debugging purpose, but from a different point of view could be see a malicious device and be a problem for a real scenario.
+	\subsection{Man in the middle}
+	A man in the middle attack could proxy the UDP traffic and change packets contents - such as the measurements or ON/OFF commands. 
+	An attacker could even change the source IP address field of some INIT packets, and so the plugs would connect to the attacker server.
+	Some tools, such as Scapy which is a Python library, allow to capture, modify and forward packets. Our system would not be able to detect that the packet has been modified, 
+	also because the UDP checksum is not enabled and so, the integrity of header and payload is not guarantee.
 

### 2021-03-26 paper/main.tex
aggiunta cazzata

@@
 	If an attacker uses a fake plug could send a random value to the system avoiding the user to turn on the correct device, considering that the system sums the energy consumption to prevent blackouts.
-An identification mechanism, for example using a token validation procedure, could be implemented to recognize and guarantee the access to authorized devices.
-An example of fake plug is the NodeMcu V3, which is used for debugging purpose, but from a different point of view could be see a malicious device and be a problem for a real scenario.
+An authentication mechanism, for example using a token validation procedure, could be implemented to recognize and guarantee the access to authorized devices.
+An example of fake plug is the NodeMcu V3, which is used for debugging purpose, but from a different point of view could be see a malicious device and be a problem in a real scenario.
+We used the NodeMcu V3 board to perform this attack, and since it is a high level threat an authentication procedure is required.
 	\subsection{Man in the middle}

### 2021-03-26 paper/main.tex
system res

@@
 	\section{System results}
-	We used Wireshark to monitor our network while running the system.
-Generally, TCP traffic worsens the performances of UDP in wireless applications.
+	Generally, TCP traffic worsens the performances of UDP in wireless applications. To check that this is not the case with our system,
+	we used Wireshark to monitor our network while it was running.
 In particular, during the test, we had both TCP and UDP third-party traffic, in particular, we had an Apex Legends game (UDP) and normal web navigation (TCP).
@@
 The traffic generated by the system is not much as can be seen in Figure~\ref{fig:grafico}.
+While the test was successful it only had two plugs, one of them simulated.
+To achieve more realistic results the simulated plug generates more traffic than a real plug.
 

### 2021-03-29 paper/main.tex
missing comma
ultime modifiche

--- 2021-03-26 paper/main.tex
@@
 	\section{State of the Art}
-	Smart plugs with power consumption detection are commonly used in the same household scenarios, but they implement different workflows and protocols.
-In fact, usually to realize these IoT devices an external platform is integrated with the main board (Arduino, Raspberry Pi, generic boards with EPS 8266) .
-In most cases, this platform is Blynk, which is a hardware-agnostic IoT platform and allows to configure our board in many different ways.
-	The user could use the cloud infrastructure provided by the Blynk company, or, since the source code is open-source, download and install their own server. 
-	This latter scenario is the preferred one since is free, and consist of the Blink server, the blink app and the smart devices, which uses Blynk API to perform the connections.
-A Blynk installation is generic-purpose, so you could install and control different types of devices and show the measurements using only the TCP protocols.
-Anyway, app user interface needs to be customized and the server needs a database, so the configuration requires much time.
-Instead, our system - as described in the following paragraphs - has a different goal and provides essential features to manage the smart plugs.
-The aim of our project is to create a functional IoT system which avoids blackouts and in the meantime has a low impact on the wireless network using a modified version of the UDP protocol.
-	Although, Blynk implements some security feature which makes it more secure respect to our system.
+	Smart plugs with power consumption detection are commonly
+	used in the same household scenarios, but they implement
+	different workflows and protocols. Usually to
+	realize these IoT devices an external platform is integrated
+	with the main-board (Arduino, Raspberry Pi, generic boards
+	with EPS 8266). In most cases, this platform is Blynk, which
+	is a hardware-agnostic IoT platform and allows us to configure
+	our board in many different ways. The user could use the
+	cloud infrastructure provided by the Blynk company, or, since
+	the source code is open-source, download and install their server. This latter scenario is the preferred one since is free
+	and consists of the Blink server, the blink app, and the smart
+	devices, which use Blynk API to perform the connections. A
+	Blynk installation is generic-purpose, so you could install and
+	control different types of devices and show the measurements
+	using only the TCP protocols. Anyway, the app user interface
+	needs to be customized and the server needs a database, so
+	the configuration requires much time. Instead, our system -
+	as described in the following paragraphs - has a different goal
+	and provides essential features to manage the smart plugs. Our project aims to create a functional IoT system that
+	avoids blackouts and in the meantime has a low impact on
+	the wireless network using a modified version of the UDP
+	protocol. Although, Blynk implements some security feature
+	which makes it more secure respect to our system.
 
 	\section{General architecture}
-	The general architecture has three main components: the smart plugs, the server, and the web interface.
-The smart plugs code have been written using Arduino IDE in C++.
-Instead, the server has been developed in Java and the web interface is written in React.
-The rundown of what each part does is made up of a WeMos D1 R2, an Arduino-like board, monitors a sensor that gathers data on the power consumption, and controls a relay that turns on or off the appliance.
-It communicates over wireless with the UDP server that keeps track of the plugs and their energy consumption.
-The web interface uses an API exposed by the server to let the user see and control the status of each plug.
+	The general architecture, represented in Figure~\ref{fig:architecture_schema}, has three main components: the
+	smart plugs, the server, and the web interface. The smart
+	plugs code has been written using Arduino IDE in C++.
+	Instead, the server has been developed in Java and the web
+	interface is written in React. The rundown of what each part
+	does is made up of a WeMos D1 R2, an Arduino-like board,
+	monitors a sensor that gathers data on the power consumption,
+	and controls a relay that turns on or off the appliance. It
+	communicates over wireless with the UDP server that keeps
+	track of the plugs and their energy consumption. The web
+	interface uses an API exposed by the server to let the user see
+	and control the status of each plug.
 	\begin{figure}[htbp]
@@
 The hardware has been chosen to be low-cost and accurate \cite{8442066}.
-	The connection scheme is represented in Figure~\ref{fig:pcbschema}, and has a cost of about €15, so it is not that expensive. The smart plug can be seen in Figure~\ref{fig:img5348}.
-	The WeMos D1 R2 board is equipped with a EPS 8266 wireless module operating at 2.4GHz.
-The connection settings are hardcoded in the software because storing it would require an SD module and an SD card.
+	The connection scheme is represented in Figure~\ref{fig:pcbschema} and has a cost of about €15, so it is not that expensive. The smart plug can be seen in Figure~\ref{fig:img5348}.
+	The WeMos D1 R2 board is equipped with an EPS 8266 wireless module operating at 2.4GHz.
+The connection settings are hard-coded in the software because storing it would require an SD module and an SD card.
 The board is programmed in C/C++ using Arduino IDE and uses the JSON format to serialize the data that will be sent, using a UDP library, to the server.
 	In every Arduino-like board, there is a function that allows our program to wait for UDP package arrivals from the server, affecting the relay status.
-	Another thread, once the board has recognized and registered the server, sends updates periodically if there is a variation greater than the 10\% of the energy consumption.
+	Another thread, once the board has recognized and registered the server, sends updates periodically if there is a variation greater than 10\% of the energy consumption.
 	First, smart plugs wait for an \textit{INIT message}, sent by the server via broadcast.
@@
 	Then, the plug starts to send \textit{UPDATE messages} to inform the server about energy consumption variation.
-To do so, a thread keeps watch over the readings provided by the PZEM sensor which integrates an ADC  system  in one integrated circuit \cite{8612412}.
+To do so, a thread keeps watching over the readings provided by the PZEM sensor which integrates an ADC  system  in one integrated circuit \cite{8612412}.
 	A summary of the interactions between plug and server is given in Figure~\ref{fig:plugserverinteraction}.
@@
 After those requests have been received correctly, the correct action is performed and then an \textit{ACK message} is sent to inform the server about the successful receipt of the command.
-	We also used a different board called NodeMcu V3 in order to simulate a plug to get a real traffic scenario with at least two plugs.
-Since, NodeMcu V3 is not connected to a PZEM module, the power consumption readings are random values.
+	We also used a different board called NodeMcu V3 to simulate a plug to get a real traffic scenario with at least two plugs.
+Since NodeMcu V3 is not connected to a PZEM module, the power consumption readings are random values.
 	\begin{figure}[htbp]
@@
 		\centering
-		\includegraphics[width=0.7\linewidth]{assets/plugserverinteraction}
+		\includegraphics[width=\linewidth]{assets/plugserverinteraction}
 		\caption{Interaction between smart plugs and server}
@@
 The information about the plugs saved by the server is kept as a \textit{thread-safe hashmap}.
-Some of this information, such as the IP address of the plugs, the type of appliance connected, and the max power consumption is also saved in a \textit{XML file} to avoid losing it in case of a server malfunction or restart.
+Some of this information, such as the IP address of the plugs, the type of appliance connected, and the max power consumption is also saved in an \textit{XML file} to avoid losing it in case of a server malfunction or restart.
 
@@
 	As we already mentioned, another challenge to face is the security issue, the information sent from a plug to the server is completely clear, so there is no encryption implemented. 
-	In fact, our aim is to create a smart system and for debugging purpose is more convenient to use un-encrypted packets.
-	 The following paragraphs describes different attacks which we have implemented or could be performed quite easily.
+	In fact, we aim to create a smart system and for debugging purpose is more convenient to use un-encrypted packets.
+	The following paragraphs describe different attacks which we have implemented or could be performed quite easily.
 	\subsection{Fake plugs}
-	A fake plug could be easily added to our system sending fake readings. In our scenario this could be a problem, because could lead to a different behavior.
+	A fake plug could be easily added to our system sending fake readings. In our scenario, this could be a problem, because could lead to different behavior.
 	If an attacker uses a fake plug could send a random value to the system avoiding the user to turn on the correct device, considering that the system sums the energy consumption to prevent blackouts.
-An identification mechanism, for example using a token validation procedure, could be implemented to recognize and guarantee the access to authorized devices.
-An example of fake plug is the NodeMcu V3, which is used for debugging purpose, but from a different point of view could be see a malicious device and be a problem for a real scenario.
+An authentication mechanism, for example using a token validation procedure, could be implemented to recognize and guarantee access to authorized devices.
+An example of a fake plug is the NodeMcu V3, which is used for debugging purpose, but from a different point of view could be seen as a malicious device and be a problem in a real scenario.
+We used the NodeMcu V3 board to perform this attack, and since it is a high-level threat an authentication procedure is required.
 	\subsection{Man in the middle}
-	A man in the middle attack could proxy the UDP traffic and change packets contents - such as the measurements or ON/OFF commands. 
+	A man in the middle attack could proxy the UDP traffic and change the content of packets - such as the measurements or ON/OFF commands. 
 	An attacker could even change the source IP address field of some INIT packets, and so the plugs would connect to the attacker server.
 	Some tools, such as Scapy which is a Python library, allow to capture, modify and forward packets. Our system would not be able to detect that the packet has been modified, 
-	also because the UDP checksum is not enabled and so, the integrity of header and payload is not guarantee.
-
+	also because the UDP checksum is not enabled and so, the integrity of the header and payload is not guaranteed.
+	\subsection{Creating interference using a magnet}
+	This last threat consists of using a magnet and gets it closer to the coil.
+The coil generates an electromagnetic field to measure the power consumption and using the magnets the measurements may change due to interference.
+This kind of attack works if there is no housing to protect the socket, and therefore also the coil.
+By using it, the magnet will not be able to alter the measurements.
+This all depends on the size of the magnet used, since we tried with a very small one and, pushing it away a little, there were no effects on the measurement.
+In the end, this attack is an open-ended question and needs further investigation.
 	\section{System results}
-	We used Wireshark to monitor our network while running the system.
 	Generally, TCP traffic worsens the performances of UDP in wireless applications.
-In particular, during the test, we had both TCP and UDP third-party traffic, in particular, we had an Apex Legends game (UDP) and normal web navigation (TCP).
+To check that this is not the case with our system, we used Wireshark to monitor our network while it was running to evaluate the impact of our traffic.
+During the test, we had both TCP and UDP third-party traffic, in particular, we had an Apex Legends game (UDP) and normal web navigation (TCP).
 The main objective of the test was to check the efficacy of our version of reliable UDP, so the focus was on the reception of acknowledgments by the server.
@@
 The traffic generated by the system is not much as can be seen in Figure~\ref{fig:grafico}.
+While the test was successful, it only had two plugs, one of them simulated.
+To achieve more realistic results the simulated plug generates more traffic than a real plug
 
